---
title: 'Assignment 5: Probabilistic Grammar'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the Libraries + Functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

The data for this project has already been loaded. Here you will be distinguishing between the uses for *let*, *allow*, and *permit*. You should pick two of these verbs to examine and subset the dataset for only those columns. You can use the `droplevels()` function to help drop the empty level after you subset.  

```{r libraries}
library(Rling)
data(let)
head(let)
```

## Description of the Data

The data is from the COCA: Corpus of Contemporary American English investigating the verb choice of *let*, *allow*, and *permit*. These are permissive constructions that are often paired with the word *to*. Predict the verb choice in the `Verb` column with the following independent variables:

  - Reg: Spok for spoken conversations, Mag for magazine articles. 
  - Permitter: semantic class of the clause subject, Anim for animate, Inanim for inanimate and Undef for undefined.
  - Imper: yes for the imperative, no for not.
  - *Note*: Year is in the dataset, which would be awesome but gave me trouble. You can try adding it if you want. 

## Sample Size Requirements

- Is the sample size large enough for four predictors? 
- Is the split between your choosen verbs even enough to think you could predict them?

```{r samplesize}

```

## Running a Binary Logistic Regression

- Run the logistic regression using the `rms` package. 
  - Use the $\chi^2$ test - is the overall model predictive of verb choice? Is it significant?
  - What is Nagelkerke's pseudo-$R^2$? What does it tell you about goodness of fit?
  - What is the C statistic? How well are we predicting?

```{r runrms}

```

## Coefficients

- Explain each coefficient - are they significant? What do they imply if they are significant (i.e., which verb does it predict)?
    - Reg:
    - Permitter: 
    - Imper: 

## Interactions

- Add the interaction between Imper and Reg by doing `Imper*Reg`, but remember you will need to do a `glm` model.
- Use the `anova` function to answer if the addition of the interaction was significant.
  - Is the interaction useful?
- Use the `visreg` library and funtion to visualize the interaction.
  - How would you explain that interaction? 
  

```{r interaction}

```

## Outliers

- Use the `car` library and the `influencePlot()` to create a picture of the outliers. 
  - Are there major outliers for this data?

```{r outliers}

```

## Assumptions

- Explore the `vif` values of the original model (not the interaction model) and determine if you meet the assumption of additivity (meaning no multicollinearity). 

```{r vif}

```
  