---
title: 'Factor Analysis'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk

```

Do the same for the Python libraries you will need. 

```{python}
##python chunk 

```

## The Data

The data is provided as `liwc_house_conflict.csv`. We collected over 1000 different speeches given on the floor of the US House of Representatives that discussed different war time conflicts with Iraq, Kuwait, Russia, Syria, Iran, and a few others. This data was then processed with the Linguistic Inquiry and Word Count software, which provides a linguistic frequency analysis for many categories. 

You should pick 15-20 categories that you think might cluster together and/or be interesting to examine for their register relatedness. You can learn more about the categories by checking out the attached manual starting on page four. Do not use the "total" categories with their subgroups or you might get a singular matrix error. You might also consider running a quick summary on your choosen categories as well, to make sure they are not effectly zero frequency (i.e., most of the informal language ones will be very small percents due to the location of the speech).

Import your data and create a data frame here with only the categories you are interested in.

```{r thedata}
##r chunk

```

Transfer the data over to python to use as well. 

```{python}
##python chunk

```

## Before you start

Include Bartlett's test and the KMO statistic to determine if you have adequate correlations and sampling before running an EFA. 

```{r beforeyougo}
##r chunk

```

Include Bartlett's test and the KMO statistic from Python. 

```{python}
##python chunk

```

QUESTION: Interpret both KMO and Barlett's test. What do they tell you about the screening for your EFA? 
ANSWER: 

## How many factors?

- Explore how many factors you should use.
  - Include a parallel analysis and scree plot.
  - Sum the Kaiser criterion.

```{r howmany}
##r chunk

```

- Include the scree plot and summation of the eigenvalues from Python. 

```{python}
##python chunk

```

QUESTION: Interpret the results from these diagnostic tests for the number of factors. What does the parallel analysis suggest? How does that compare to the scree plot and Kaiser criterion results? How many factors should you use? 
ANSWER: 

## Simple structure - run the EFA

- Run the EFA in both R and Python.
  - Include the saved `fa` code, but then be sure to print out the results, so the summary is on your report.
  - Plot the results from your analysis. 

```{r runit}
##r chunk
##save it

##print it out

##plot the results
```

- For Python, run the factor analysis and print out the loadings. 

```{python}
##python chunk

```

QUESTION: Interpret the results from your EFA. How do the items group together? What do those results imply? What where the bad items? Were you able to achieve simple structure? 
ANSWER: 

## Adequate solution

QUESTION: Examine the fit indice(s). Are they any good? How might you interpret them?
ANSWER: 

QUESTION: Examine the results - what do they appear to tell you? Are there groupings of variables in these analyses that might explain different structures/jargons/registers in language we find in Congress? 
ANSWER: 

QUESTION: What other information might you include in this analysis to better understand the dynamics of Congress and their speech? 
ANSWER: 