---
title: 'Assignment 3: Association'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create the Data

- One of the corpora here: https://corpus.byu.edu/corpora.asp 
- Collect two bigrams that you can compare using the association measures listed (does not have to be X-Y, Z-Y, but that would help you compare them)
- Create a dataframe like the one from lecture of those bigrams

```{r createdata}

```

## Load the Libraries + Functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libraries}

```

## Attraction and Reliance

Calculate the attraction for your bigrams.

```{r attract}

```

Calculate the reliance for your bigrams.

```{r reliance}

```

## Log Likelihood

Calculate the LL values for your bigrams.

```{r LL}

```

## Pointwise Mutual Information

Calculate the PMI for your bigrams. 

```{r PMI}

```

## Odds Ratio

Calculate the OR for your bigrams. 

```{r OR}

```

## Interpret your results

Given the statistics you have calculated above, what is the relation of your bigrams? Write a short summary of the results, making sure to answer the following: 

- Are they related?
- Do they attract or repel each other?
- Are there differences between the separate bigrams?


