---
title: 'Set Up Your Virtual Machine'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

## Virtual Machine Set Up Guide

Go to: https://rstudio.thedoomlab.com/auth-sign-in

Your log in is:

  -	Username: firstname_lastname
  -	Password: firstnameidnumber
  -	Fill in first and last name with your first and last name, while ID number is your HU ID number.

### Python Set Up

- Click on terminal (next to the console) and run the following lines WITHOUT THE DASH IN THE FRONT: 
  
  - pip3 install -U spacy==2.3.7
  - python3 -m spacy download en_core_web_sm
  - pip3 install nltk
  - pip3 install gensim
  - pip3 install contractions
  - pip3 install textblob
  - pip3 install afinn
  - pip3 install pyLDAvis
  - python3 -m nltk.downloader nps_chat
  - python3 -m nltk.downloader webtext
  - python3 -m nltk.downloader brown
  - python3 -m nltk.downloader sentiwordnet
  - python3 -m nltk.downloader vader_lexicon
  - python3 -m nltk.downloader popular
  - pip3 install sklearn --force-reinstall

### Special R Package 

Run the following in the R console WITHOUT THE DASH (ensure the quotes copy correctly):

  - devtools::install_github("bnosac/RDRPOSTagger", force = TRUE)

### Turn off Miniconda

###################################################
###################################################
###################################################
###################################################
########### IMPORTANT BE SURE TO SAY NO ########### 
###################################################
###################################################
###################################################
###################################################

When you run py_config() the first time, it will ask you to install miniconda. Say no! We already have python3 installed on the server. 

YOU WILL NEED TO SAY NO IN THE CONSOLE PLEASE STOP AND LOOK AT THE CONSOLE. 

```{r}
##r chunk
library(reticulate)
py_config()
#SAY NO SAY NO SAY NO
```

If you get to this section, and it says miniconda is your python, you have made a mistake. Contact your instructor. 

### Let's do some R

- In this chunk, we will load a dataset - use `data(rock)` to load it. 
- Use the `head()` function to print out the first six rows of the dataset. 

```{r an_r_section}
##r chunk

```

### Call a dataset in Python

- First, load the `sklearn` library, it has several sample datasets. You load python packages by using `import PACKAGE`. Note that you install and call this package different names (scikit-learn = sklearn).
- Next, import the datasets part of sklearn by doing `from PACKAGE import FUNCTION`. Therefore, you should use `from sklearn.datasets import fetch_california_housing`. 
- Then call the `housing` dataset by doing: `housing = fetch_california_housing()`.
- To print out the first six rows, use the `.head()` function: `df_housing.head()`, after converting the file with `pandas` (code included below).

```{python}
##python chunk
##TYPE HERE##


##convert to pandas
import pandas as pd
df_housing = pd.DataFrame(data = housing.data, 
                         columns = housing.feature_names)

```

QUESTION: Check out the environment windows - you should have one for R and one for Python. What differences do you see? 
ANSWER: 

## Print out Python information in R

- You can have the two environments interact. To print out information from Python in R: `py$VARNAME`.
- Normally, to print out R dataset columns, you do `DATAFRAME$COLUMN`. 
- First, figure out the column names from your data frame using `colnames()`.
- Print out the first 10 rows of one of the columns in *R* below. 

```{r}
##r chunk


```

## Print our R in Python

- When using R in Python, instead of `$`, we use `.` like this: `r.VARNAME`. 
- To print out a single column, you use `DATAFRAME["COLUMNNAME"]` or `DATAFRAME.COLUMNNAME`. 
- First, figure out the column names using `DATAFRAME.columns`.
- Then print out the first 10 rows of that column in python below. 

```{python}
##python chunk

```

## Get started with PyCharm!

- Great job! Here's what you learned:
  - You know how to install and load the libraries in both languages.
  - You know how to load built in datasets in both languages.
  - You know how to print out data from one language to another. 
- Turn this document in for credit --> hit KNIT --> turn in the HTML file.
- Be sure to fill in your name at the top!
- Be sure to answer the embedded questions!
