---
title: 'Classification'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Please do not reorder the assignment - fill in each chunk as requested. 

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
```

Load the Python libraries or functions that you will use for that section. 

```{python}
##python chunk

```

## The Data

The dataset is a set of Youtube comments that have been coded as:
  - 1: spam youtube messages 
  - 0: good youtube messages
  - This data is stored in the `CLASS` column

Import the data using either R or Python. I put a Python chunk here because you will need one to import the data, but if you want to first import into R, that's fine. 

```{python}
##python chunk

```

## Clean up the data (text normalization)

Use one of our clean text functions to clean up the `CONTENT` column in the dataset. 

```{python}
##python chunk

```

## Split the data

Split the data into testing and training data.

```{python}
##python chunk

```

## Process the data

For word2vec, create the tokenized vectors of the text.

```{python}
##python chunk

```

## TF-IDF

Create a TF-IDF matrix.

```{python}
##python chunk

```

## Word2Vec

Build the word2vec model.

```{python}
##python chunk

```

## Convert the model

Convert the word2vec model into a set of features to use in our classifier. 

```{python}
##python chunk

```

## Build a classifier model

In class, we used a few algorithms to test which model might be the best. Pick *one* of the algorithms to use here (logistic regression, naive bayes, support vector machine). 

Run your algorithm on both the TF-IDF matrix and the output from word2vec. 

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of both of your models.

```{python}
##python chunk

```

## Interpretation 

- Where you able to predict the spam messages from the real comments?
- Which model provided you with a better prediction?