---
title: 'Word2Vec'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
```

Load the Python libraries or functions that you will use for that section. 

```{python}
##python chunk

```

## The Data

The dataset is a set of text messages that have been coded as:
  - "ham": normal text messages
  - "spam": bad text messages

Import the data using either R or Python. I put a Python chunk here because you will need one to import the data, but if you want to first import into R, that's fine. 

```{python}
##python chunk

```

## Clean up the data

Use one of our clean text functions to clean up the text column in the dataset. 

```{python}
##python chunk

```

## Split the data

Split the data into testing and training data.

```{python}
##python chunk

```

## Process the data

For FastText and word2vec, create the tokenized vectors of the text.

```{python}
##python chunk

```

## Word2Vec

Build the word2vec model.

```{python}
##python chunk

```

## Convert the model

Convert the model into a set of features to use in our classifier. 

```{python}
##python chunk

```

## Build a classifier model

In class, we used logistic regression to classify the data. You can use any machine learning algorithm you want here, and build a classification model. 

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

## Build a FastText model

Using the same data, build a FastText model.

```{python}
##python chunk

```

## Extract the features

Convert the FastText model into features for prediction.

```{python}
##python chunk

```

## Build a classifier model

Using the same machine learning algorithm as above, build a classifier model that uses the FastText data to predict the categories.

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

## Interpretation 

- Where you able to predict which messages were spam and which were ham?
- Which model provided you with a better prediction?