---
title: 'Word2Vec'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
```

Load the Python libraries or functions that you will use for that section. 

```{python}
##python chunk

```

## The Data

The dataset is a set of Youtube comments that have been coded as:

  - 1: spam youtube messages 
  - 0: good youtube messages
  - This data is stored in the `CLASS` column.

Import the data in either R or Python. Convert your dataframe into a Python `pandas` dataframe for this assignment. 

```{python}
##python chunk

```

## Clean up the data

Use one of our clean text functions to clean up the `CONTENT` column in the dataset. 

```{python}
##python chunk

```

## Split the data

Split the data into testing and training data.

```{python}
##python chunk

```

## Process the data

For FastText and word2vec, create the tokenized vectors of the text.

```{python}
##python chunk

```

## Word2Vec

Build the word2vec model.

```{python}
##python chunk

```

## Convert the model

Convert the model into a set of features to use in our classifier. 

```{python}
##python chunk

```

## Build a classifier model

In class, we used logistic regression to classify the data. You can use any machine learning algorithm you want here, and build a classification model. 

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

## Build a FastText model

Using the same data, build a FastText model.

```{python}
##python chunk

```

## Extract the features

Convert the FastText model into features for prediction.

```{python}
##python chunk

```

## Build a classifier model

Using the same machine learning algorithm as above, build a classifier model that uses the FastText data to predict the categories.

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

## Interpretation 

- Where you able to predict the spam messages from the real comments? 
- Which model provided you with a better prediction?