---
title: 'Word2Vec'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk
```

Load the Python libraries or functions that you will use for that section. 

```{python}
##python chunk

```

## The Data

The dataset is a set Amazon Reviews that have been coded as:

  - __label1__: Fake review 
  - __label2__: Real review 
  - This data is stored in the `LABEL` column.

Import the data in either R or Python. Convert your dataframe into a Python `pandas` dataframe for this assignment. 

```{python}
##python chunk

```

## Clean up the data

Use one of our clean text functions to clean up the `REVIEW_TEXT` column in the dataset. 

```{python}
##python chunk

```

QUESTION: Given the data, what cleaning options did you choose? Why would you use those options and not others? 
ANSWER: 

## Split the data

Split the data into testing and training data.

```{python}
##python chunk

```

## Process the data

For FastText and word2vec, create the tokenized vectors of the text.

```{python}
##python chunk

```

## Word2Vec

Build the word2vec model - consider the number of dimensions you think you should use to predict the fake versus real reviews, as well as if you should use CBOW or SkipGram modeling. 

```{python}
##python chunk

```

QUESTION: Why did you chose the number of dimensions you did for the model?
ANSWER: 

QUESTION:
ANSWER: What type of model do you think will predict better for the reviews: CBOW or SkipGram and indicate why. 

## Convert the model

Convert the model into a set of features to use in our classifier. 

```{python}
##python chunk

```

## Build a classifier model

In class, we used logistic regression to classify the data. You can use any machine learning algorithm you want here, and build a classification model. 

```{python}
##python chunk

```

QUESTION: What algorithm did you choose and why? 
ANSWER: 

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

QUESTION: Interpret the results from your model. Was it able to predict the reviews? 
ANSWER: 

## Build a FastText model

Using the same data, build a FastText model with the same parameters as chosen above. 

```{python}
##python chunk

```

## Extract the features

Convert the FastText model into features for prediction.

```{python}
##python chunk

```

## Build a classifier model

Using the same machine learning algorithm as above, build a classifier model that uses the FastText data to predict the categories.

```{python}
##python chunk

```

## Examine the results

Print out the accuracy, recall, and precision of your model.

```{python}
##python chunk

```

QUESTION: Interpret the results from your model. Was it able to predict the reviews? 
ANSWER: 

## Interpretation 

QUESTION: Where you able to predict the spam messages from the real comments? 
ANSWER: 

QUESTION: Which model provided you with a better prediction?
ANSWER: 