---
title: 'Set Up Your Computer or Virtual Machine'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

For this semester, you have two options:

- Use your own computer.
  - If you have an older machine, you are likely to have problems with some of the installation of packages. If you have a MacBook Air or other "mini" type machine, you will potentially find you do not have the space for the installed packages. 
  - I will help you troubleshoot during the completion of this assignment, but all other problems (and later in the semester) you will need to use google/stack overflow/etc. to fix for yourself. 
  
- Use the provided RStudio virtual machine. 
  - https://class.aggieerin.com/auth-sign-in
  - Nearly all packages have been installed for you already!
  - Be sure to save your work on your own machine as well, this server is reset at the end of each semester. 

**Only complete the part of the assignment based on your choice for computer or virtual machine!!**

## Your Own Computer 

### Install Software

- Most recent version of R: https://cloud.r-project.org/
- Most recent version of RStudio: https://rstudio.com/products/rstudio/download/#download
- Java JDK: https://www.oracle.com/technetwork/java/javase/downloads/index.html
- Most Recent Java: https://www.java.com/en/

```{r}
##r chunk - do not change these
R.version
#RStudio.Version() run this line but it won't knit with it "on"
```

ANSWER: What version of Rstudio are you using? Please note it should be the latest version! 

### Install all the R Packages

- Install the following packages, that you will need all semester:
- markdown, knitr, reticulate, party, ca, FactoMineR, rgl, rms, visreg, pvclust, car, boot, psych, ngram, LSAfun, tm, topicmodels, tidytext, tidyverse, ggraph, igraph, memnet, widyr, stringdist
- Run this: Sys.setenv(TZ = "America/New_York") if you see the TZ errors. 
- You may need to pay attention to the rlang package, I had to uninstall rlang and reinstall it. 
- Do not include code for knitting purposes. 

### Install the special R Packages

- Use the following code to install the special packages for R. 
- Change `eval = TRUE` to `eval = FALSE` once you have them installed. 

```{r eval = TRUE}
install.packages("https://osf.io/ak7gq/download", repos = NULL, method = "libcurl", type = "source")
```

### Set up your python

- Load the `reticulate` library.

```{r python_setup}
##r chunk

```

### Install Miniconda

Try typing `py_config()` below. You should get a prompt to install Miniconda. If not, use `install_miniconda()`.

```{r}
##r chunk

```

### Show you've installed Python

Run `py_config()` in the *R* chunk below. 

```{r}
##r chunk

```

### Windows Machines

Windows machines need special programs to make all this work: 

- Rtools: https://cran.r-project.org/bin/windows/Rtools/ 
- Visual Studio Build Tools 2019: https://visualstudio.microsoft.com/downloads/#build-tools 
- WordNet: https://wordnet.princeton.edu/download/current-version

### Install Python Packages

- Install the python packages by typing in R (the reticulate library must be loaded!): `py_install("package_name", pip = T)`
- Change `eval = TRUE` to `eval = FALSE` once you have them installed. 

Packages: nltk, matplotlib, PyQt5, scikit-learn, numpy, pandas, prince, factor-analyzer, gensim, pyLDAvis, bs4

```{r eval = TRUE}

```

### Special Python Extras

For nltk, you will need to add a few other pieces. Type the following into R console: 
 - library(reticulate)
 - repl_python() 
 - Here you should notice you have switched from > to >>> which indicates you are in Python:

  - import nltk
  - nltk.download("popular")
  - nltk.download("nps_chat")
  - nltk.download("webtext")
  - nltk.download("abc")

To get out of >>> python, type exit or hit the Esc key.

Click on terminal > type in:
   - python -m spacy download en_core_web_sm
   - This will download the English language spacy module.
   - pip install lxml

## Virtual Machine

Go to: https://class.aggieerin.com/auth-sign-in

Your log in is:

  -	Username: firstname_lastname
  -	Password: firstnameidnumber
  -	Fill in first and last name with your first and last name, while ID number is your HU ID number.

### Python Set Up

- Click on terminal and run the following lines:
  
  - pip3 install -U spacy
  - python3 -m spacy download en_core_web_sm
  - pip3 install nltk
  - pip3 install gensim
  - python3 -m nltk.downloader popular
  - pip3 install prince
  - pip3 install factor-analyzer
  - pip3 install pyLDAvis
  - python3 -m nltk.downloader abc

### Turn off Miniconda

When you run py_config() the first time, it will ask you to install miniconda. Say no! We already have python3 installed on the server. 

```{r}
##r chunk
library(reticulate)
py_config()
```

## Everyone

### Let's do some R

- In this chunk, we will load a dataset - use `data(rock)` to load it. 
- Use the `head()` function to print out the first six rows of the dataset. 

```{r an_r_section}
##r chunk

```

### Call a dataset in Python

- First, load the `sklearn` library, it has several sample datasets. You load python packages by using `import PACKAGE`. Note that you install and call this package different names (scikit-learn = sklearn).
- Next, import the datasets part of sklearn by doing `from PACKAGE import FUNCTION`. Therefore, you should use `from sklearn import datasets`. 
- Then call the `boston` dataset by doing: `dataset_boston = datasets.load_boston()`.
- To print out the first six rows, use the `.head()` function: `df_boston.head()`, after converting the file with `pandas` (code included below).

```{python}
##python chunk
##TYPE HERE##

##convert to pandas
import pandas as pd
df_boston = pd.DataFrame(data=dataset_boston.data, columns=dataset_boston.feature_names)
```

QUESTION: Look in your environment window. What do you see?

## Print out Python information in R

- You can have the two environments interact. To print out information from Python in R: `py$VARNAME`.
- Normally, to print out R dataset columns, you do `DATAFRAME$COLUMN`. Try to print out the `CRIM` column from your `df_boston` variable. 

```{r}
##r chunk

```

## Print our R in Python

- When using R in Python, instead of `$`, we use `.` like this: `r.VARNAME`. 
- To print out a single column, you use `DATAFRAME["COLUMNNAME"]`. Try printing out the `shape` column in the `rock` dataset. 

```{python}
##python chunk

```

## Get started with PyCharm!

- Great job! Here's what you learned:
  - Installed Python!
  - You know how to install and load the libraries in both languages.
  - You know how to load built in datasets in both languages.
  - You know how to print out data from one language to another. 
- Turn this document in for credit --> hit KNIT --> turn in the HTML file.
- Be sure to fill in your name at the top!
- Be sure to answer the embedded questions!

  

