---
title: 'Correspondence Assignment'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libaries}
##r chunk

```

```{python}
##python chunk

```

## Simple Correspondence Analysis

### The Data

Women and metonymy in Ancient Chinese: the data concerns metonymic patterns that were used to refer to women in texts of the Ming dynasty in China (1368 – 1644). The rows are different types of female referents, namely, imperial woman (queen or emperor's concubine), servant girl, beautiful woman, mother or grandmother, unchaste woman (prostitute or mistress), young girl, wife (or concubine). The columns are six metonymic patterns:

- Action for agent or patient, e.g. "to ruin state" for "beautiful woman"
- Body part for whole, e.g. "powder-heads" for "prostitutes"
- Location for located, e.g. "the middle palace" for "queen"
- A piece of clothing for person, e.g. "red dress" for "beautiful woman"
- Characteristic for person, e.g. "respectable-kind" for "mother"
- Possessed for possessor, e.g. "blusher and powder" for "beautiful woman"

Import the data and create a mosaic plot to visualize the differences in usage across women references. 

```{r}
##r chunk

```

QUESTION: Write a summary paragraph of the interpretation of your mosiac plot. You should detail which words are more or less frequent that expected, how the terms appear to go together, and provide this analysis in plain English.
ANSWER: 

### The Analysis

Run a simple correspondence analysis on the data. 

```{r}
##r chunk 

```

QUESTION: What do the inertia values tell you about the dimensionality of the data?
ANSWER: 

Create a 2D plot of the data. 

```{r}
##r chunk

```

QUESTION: What can you tell about the word usage from examining this plot? Provide an interpretation of the clustering and groupings that appear to occur in the data. 
ANSWER: 

## Multiple Correspondence Analysis

The data included is from a large project examining the definitions of words, thus, exploring their category requirements. The following columns are included:

- Cue: the word participants saw in the study, what they gave a definition for.
- POS_Cue: the part of speech of the cue word.
- POS_Feature: the part of speech for the feature word they listed (i.e. zebra-stripes, stripes would be the feature).
- POS_Translated: these features were then translated into a root form, and this column denotes the part of speech for the translated word.
- A1 and A2: the type of affix that was used in the feature. For example, ducks would be translated to duck, and the difference is a numerical marker for the affix of s.

Run a multiple correspondence analysis on the data, *excluding* the cue column. 

```{r}
##r chunk

```

Plot the variables in a 2D graph. Use `invis = "ind"` rather than `col.ind = "gray"` so you can read the plot better. 

```{r}
##r chunk

```

QUESTION: What clusters do you see involved in this graph? Are there some predictors that are separated from the rest?
ANSWER:

### Simple Categories

To view simple categories like we did in the lecture, try picking a few words out of the dataset that might be considered similar. I've shown how to do this below with three words, but *you must change these to be your own*.  Change the words and the `DF` to your dataframe name. We will overlay those as supplemental variables. 

You will not get credit for this section if you do not change the words into your *own* words - remember, not the ones you found on some previous assignment. Use the viewer or print out the `cue` column to view the options. 

```{r}
##r chunk
#pick a few several interesting words 
words <- c("mom", "family", "relative")

mca_model2 <- MCA(DF[DF$cue %in% words, ], 
                 quali.sup = 1, #supplemental variable
                 graph = FALSE)
```

Create a 2D plot of your category analysis. 

```{r}
##r chunk 

```

QUESTION: Interpret your plot. What features appear to be associated with each category term? 
ANSWER:

Add the prototype ellipses to the plot. 

```{r}
##r chunk

```

QUESTION: Interpret your plot. Do these items have distinct prototypes? 
ANSWER:

Create a 95% CI type plot for the category.

```{r}
##r chunk

```

QUESTION: Interpret your plot. Do these items appear to be in overlapping categories or are they similar. 
ANSWER:

## Run a MCA in Python

In this section, run the same MCA from above in Python. Include the MCA code and print out the inertia values for your analysis. 

```{python}
##python chunk 

```

## Plot the Results

Plot the results of your MCA using Python in the section below. I have included Python code below that will help if you are completing this assignment on the cloud.

```{python}
##python chunk
import matplotlib
matplotlib.use('Agg')

```

## Explore the differences

QUESTION: Do the R and Python results from the MCA show you the answer? Do you detect any differences between the outputs? You should provide a paragraph here in plain English exploring both the inertia and MCA plot results. 
ANSWER: 