---
title: "6 CFA: Basics"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Confirmatory Factor Analysis Practice Assignment

In the section below, you should load the `lavaan` and `semPlot` libraries. The data is included in `assignment_cfabasics.csv`, and you should load that dataset. 

```{r}

```

## The Data

The data represents a 30-item questionnaire called CAAFI: Computer Aversion, Attitudes, and Familiarity Index. This questionnaire includes items on computer usage, attitudes, and familiarity. 

- Computer Familiarity: Items 3, 13-14, 16, 20-23, 27, and 30. 
- Computer Attitudes: Items 1-2, 4-5, 8, 11, 18-19, and 28-29.
- Computer Aversion: Items 6-7, 9-10, 12, 15, 17, and 24-26.

Here are the items that are present on the survey: 

1. I enjoy using computers.
2. Being able to use a computer is important to me.
3. I keep up with the latest computer hardware.
4. Computers are beneficial because they save people time.
5. I like using word-processing programs.
6. I feel like a fool when I am using a computer and others are around.
7. I am smart enough to use a computer.
8. I avoid using computers whenever possible.
9. I do not understand how to use computer software (e.g., word-processing
programs, spreadsheet programs, etc.).
10. I feel that I understand how to use computer files, documents, and folders.
11. I use a computer input device every day (e.g., a keyboard, a touch pad, a mouse).
12. I can use a computer to successfully perform tasks.
13. I can add new hardware to a computer.
14. I enjoy reading computer magazines.
15. When I use a computer, I am afraid that I will damage it.
16. I enjoy connecting new computer accessories.
17. I must have a reference manual or a help file to run computer software.
18. E-mail is an easy way to communicate with people.
19. I use e-mail every day.
20. I am comfortable changing (installing/upgrading) computer software.
21. I often read computer books.
22. My friends often ask me computer-related questions.
23. I often read computer magazines.
24. Overall, I feel that I don’t know how to use a computer.
25. Computers are too scientific for me.
26. When using a computer, I often lose data.
27. I enjoy learning to use new software programs.
28. I like to use computer input devices such as a keyboard, a touch pad, a mouse,
etc.
29. Using a computer is entertaining.
30. I keep up with the latest computer software.

## Build a Model

In this section, create a one-factor model of all of the items together. 

```{r}

```

In this section, create a three-factor model based on the items proposed grouping listed above.

```{r}

```

## Analyze Your Model

Analyze both the one-factor and three-factor model.

```{r}

```

## Summarize Your Model

Include a summary of the one-factor and three-factor model with standardized output, rsquare values, and fit.measures. 

```{r}

```

## Diagram Your Model

Include a diagram for the three-factor model. Use the `what` and `edge.color` arguments to denote the strongest paths. 

```{r}

```

## Compare Models 

Use the `anova()` function and the `fitmeasures()` to create a model comparison. 

```{r}

```

QUESTION: Which model is better? 
ANSWER:

## Clean Output

Use either `model_parameters` or `broom`'s `tidy` function to neatly print out the model parameters for the three-factor model.

QUESTION: Looking at the item loadings, are any of the items poor (i.e., they do not strongly relate to their factor)?
ANSWER:

QUESTION: Looking at the correlation table, do you think these are three separate factors? 
ANSWER:

## Modifications

Include the potential modification indices for the three-factor model. Be sure to use the `sort` option to see the strongest modification indices. 

```{r}

```

QUESTION: What potential indices do you see in these modification indices? What questions may be asking the same material twice? 
ANSWER:

