---
title: "Logistic Regression"
author: "Erin M. Buchanan"
date: "01/29/2020"
output:
  slidy_presentation:
    increment: yes
---

```{r echo = F}
options(scipen = 999)
```

## Language Topics Discussed

- Grammatical slots: how can we predict what word should come next?
- Understanding word choice based on contextual features

## Synonyms

- How do we decide which word to use when we have multiple words that share the same meaning?
- I ____ to go to the mall this week.
  - Planned
  - Decided
  - Scheduled
  - am going to go 
- She is very _____.
  - Pretty
  - Beautiful
  - Alluring

## More examples

- May versus might: depending on certainty
- Gown versus dress: formality in social situation
- Soda versus coke versus pop: cultural factors

## Causative Constructions

- Phrases like: might/have/get/cause X to do Y
- Combines conjugated 'to have' or 'to get' +  direct object + main verb
- When one does not carry out an action oneself but rather has the action done by someone else
- I *had* him *paint* my house.
- Causee is the actor, does the action
- Causer is the person/thing who required the action

## Causative Constructions

- Do versus let in Dutch
- Do appears to be a direct causation
  - "If the energy is put in, the result is inevitable"
  - He reminded me of my father (causation is involuntary)
- Let appears to be an indirect causation
  - Enablement and permission
  - I let him paint my house 

## Cause for Cause

- Verb:
  - State or action: does it apply to state verbs or action verbs
  - Transitivity: why types of verbs, transitive, intransitive or both?
  
## Cause for Cause

- The action being caused:
  - Control: does the causee have control?
  - Volition: does the causee act willingly?
  - Affectedness: how is the causee affected?
  
## Cause for Cause

- Related to the causer:
  - Directness: of the causer
  - Intention: accidental or intentional
  - Natural: natural activity or with effort
  - Involvement: the causer's involvement in activity

## Criteria for Do Let

- Inducive: mental causer (human) to mental causee (let)
- Volitional: mental causer to non-mental causee (neither)
- Affective: non-mental causer to mental causee (do)
- Physical: non-mental causer to non-mental causee (do)

## Logistic Regression

Linear regression model examining a continuous outcome measure y:

$${\hat{y_i}} = b_0 + b_1x_{1i} + b_2x_{2i} ... + \epsilon_i$$
Logistic regression model examining a categorical outcome measure y:

$$g(y) = b_0 + b_1x_{1i} + b_2x_{2i} ... + \epsilon_i$$

## Logistic Regression

- Main distinction is g(y): which is the logit or log odds of the outcome. 
- Two options: binomial logistic regression
- More than two options: multinomial or polytomous regression 
- g(y) represents the odds of one choice over another. 

## Logistic Regression

- Otherwise, information is the same as a linear model:
  - $b_0$: intercept, chances of outcome when all predictors are zero
  - $b_1$: slope for one X variable, coefficient
  - ... etc. But we will also add better interpretation for the predictors to help understand likelihood of outcome (i.e., since the data is categorical)

## Requirements for Logistic Regression

- Large enough sample size for the outcome variable
- How big? 

```{r}
##r chunk
library(Rling)
data("doenLaten")
table(doenLaten$Aux)
```

## Running a Binary Logistic Regression

```{r, message=FALSE}
##r chunk
#install.packages("rms") #if you have not used it before
library(rms)
#you can also use glm() for log regression but rms has cool options
head(doenLaten)
```

## Run your model!

```{r}
##r chunk
model = lrm(Aux ~ Causation + EPTrans + Country, #model formula like lm()
            data = doenLaten)
model
```

## Frequency

- Important for data screening

```{r}
##r chunk
model$freq
```

## Overall Predictiveness

- Likelihood ratio test = $\chi^2$ test
- Similar to the F-test in regression
- $\chi^2$(5) = 271.35, p < .001
- Compared to a model of no predictors, should have less error (deviance)

```{r}
##r chunk
model$stats
```

## Goodness of Fit

- Effect size of how well the model fit the data
- $R^2$ - much like regression, albeit more difficult to interpret. 
  - In the output that's Nagelkerke's pseudo-$R^2$

```{r}
##r chunk
model$stats
```

## Goodness of Fit

- Concordance index C
  - For each $Y_i$, a probability of the outcome is created
  - C is the number of times that the probability of the outcome matches the actual outcome
- Interpretation:
  - < .5: no discrimination
  - .7 <= C < .8: acceptable
  - .8 <= C < .9: excellent
  - <= .9 outstanding

## Coefficients

- Under Coef, these are represented as log odds 
- Odds ratios are centered around one (like 6 to 1, 4 to 1)
- Log odds ratio are centered around zero
  - Positive numbers indicate a higher probability for the coded group
  - Negative numbers indicate a higher probability for the comparison group 
- What is coded versus comparison?

```{r}
##r chunk
levels(doenLaten$Aux)
```

## Coefficients

```{r}
#model
 #                      Coef    S.E.   Wald Z Pr(>|Z|)
 # Intercept             1.8631 0.3771  4.94  <0.0001 
 # Causation=Inducive   -3.3725 0.3741 -9.01  <0.0001 
 # Causation=Physical    0.4661 0.6275  0.74  0.4576  
 # Causation=Volitional -3.7373 0.4278 -8.74  <0.0001 
 # EPTrans=Tr           -1.2952 0.3394 -3.82  0.0001  
 # Country=BE            0.7085 0.2841  2.49  0.0126  
```

## Coefficients

```{r}
##r chunk
 # Causation=Inducive   -3.3725 0.3741 -9.01  <0.0001 
 # Causation=Physical    0.4661 0.6275  0.74  0.4576  
 # Causation=Volitional -3.7373 0.4278 -8.74  <0.0001 

table(doenLaten$Aux, doenLaten$Causation)
```

## Coefficients

```{r}
##r chunk
 # EPTrans=Tr           -1.2952 0.3394 -3.82  0.0001  
 # Country=BE            0.7085 0.2841  2.49  0.0126  

table(doenLaten$Aux, doenLaten$EPTrans)
table(doenLaten$Aux, doenLaten$Country)
```

## Interactions

```{r}
##r chunk
model1 = glm(Aux ~ Causation + EPTrans + Country, #model formula like lm()
             family = binomial,
             data = doenLaten)
model2 = glm(Aux ~ Causation + EPTrans*Country, #model formula like lm()
             family = binomial,
             data = doenLaten)
anova(model1, model2, test = "Chisq")
```

## Interactions

```{r}
#summary(model2)
# Coefficients:
#                     Estimate Std. Error z value             Pr(>|z|)    
# (Intercept)           2.0991     0.4079   5.146          0.000000267 ***
# CausationInducive    -3.4463     0.3892  -8.854 < 0.0000000000000002 ***
# CausationPhysical     0.3898     0.6336   0.615              0.53839    
# CausationVolitional  -3.7795     0.4364  -8.661 < 0.0000000000000002 ***
# EPTransTr            -1.8825     0.4919  -3.827              0.00013 ***
# CountryBE             0.3693     0.3416   1.081              0.27966    
# EPTransTr:CountryBE   1.0827     0.6215   1.742              0.08149 .  
```

## Interactions

```{r}
##r chunk
library(visreg)
visreg(model2, "EPTrans", by = "Country")
```

## Outliers

```{r message = F}
##r chunk
library(car)
influencePlot(model1)
```

## Assumptions

- Observations are independent
- No multicollinearity (remember VIF > 5 or 10 is bad)
- Overprediction (complete/quasi complete separation)

```{r}
##r chunk
rms::vif(model) #use the rms:: to distinguish between car::vif and rms::vif
```

## A Python Application

- Load the reticulate library to get started in Python

```{r}
##r chunk
library(reticulate)
```

## Format the data

- *R* naturally does dummy coding on character or factor labeled columns
- In Python, we have to figure these out ourselves
- We can use the `get_dummies` option to do dummy coding  

## Format the data 

```{python}
##python chunk
import pandas as pd

X = pd.get_dummies(r.doenLaten[["Causation", "EPTrans", "Country"]])
y = pd.get_dummies(r.doenLaten["Aux"])

X.head()
X.columns
X = X[['Causation_Inducive', 'Causation_Physical',
       'Causation_Volitional', 'EPTrans_Tr', 'Country_BE']]
y = y['doen']
```

## Build a logistic model 

```{python}
##python chunk
from sklearn.linear_model import LogisticRegression

# build a blank model
logreg = LogisticRegression(solver = 'lbfgs')

# fit the model with data
logreg.fit(X,y)
```

## Examine model fit

```{python}
##python chunk
# look at the predicted category
y_pred = logreg.predict(X)

#how accurate are we?
from sklearn import metrics
metrics.confusion_matrix(y, y_pred)
metrics.accuracy_score(y, y_pred)
```

## Examine coefficients

- Print out the coefficients from the model
- Print out the X column names so you can remember what they were

```{python}
logreg.coef_
X.columns
```

## A caveat

- Python logistic modeling is often used as a machine learning algorithm
- As such, the metrics for traditional statistics are not as easily programmed
- We will use this code later in the semester to predict categories in a "python" way

## Summary

- We can model word choice with various predictors by using logistic regression with two outcomes.
  - You can extend that to multinomial logistic regression with `mlogit` 
  - https://www.youtube.com/watch?v=c78eMWw43I0 is a tutorial from Dr. B (if you are interested for your final project)
- You learned how to run and use a logistic regression, along with assumptions checks and understanding the output


