---
title: "Processing Raw Text"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: 
  slidy_presentation:
    increment: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Working with strings

- Language data is just a bunch of strings!
- Strings are character vectors - but they come in lots of shapes and sizes.
- So, we will learn how to work with them in a few ways. 

```{r}
##r chunk
library(reticulate)
py_config()
```

```{python echo = F}
import platform
if platform.system() == "Windows":
    import os
    os.environ[ 'MPLCONFIGDIR' ] = '/tmp/'
    os.environ['SCIKIT_LEARN_DATA'] = "C:/Users/EBuchanan.HU/py_stuff"
```

## Basic operations

- How do we combine strings? 

```{r}
##r chunk
string1 = "swiss"
string2 = "cheese"

c(string1, string2) #notice this is a vector

paste(string1, string2, sep = " ")
```

```{python}
##python chunk
string1 = "swiss"
string2 = "cheese"

string1 + string2
string1 + " " + string2

" ".join([string1, string2])
```

## Indexing

- Indexing is calling a particular row, column, or spot in a set of objects

```{r}
##r chunk
string1[1] #pulls the first item
setofstrings = c("swiss", "cheese", "is", "great")
setofstrings[2]
setofstrings[-2]
```

```{python}
##python chunk
string1[1]
string1[0]
string2[-1]

setofstrings = ["swiss", "cheese", "is", "great"]
setofstrings[0]
setofstrings[-1]
```

## Slicing 

- Slicing is taking only a set of indices (rather than everything)

```{r}
##r chunk
setofstrings[1:2]
#setofstrings[:2] not allowed
```
```{python}
##python chunk
setofstrings
setofstrings[0:1]
setofstrings[:1]
setofstrings[:2]
setofstrings[2:]
```

## Methods

- How can we manipulate text? The ultimate goal is to clean the text, but what are some functions we might use?

```{r}
##r chunk
sentence = paste(setofstrings, collapse = " ")

toupper(sentence)
tolower(sentence)

library(stringr)
str_to_upper(sentence)
str_to_lower(sentence)
str_to_title(sentence)
str_to_sentence(sentence)
```

```{python}
##python chunk
sep = " "
sentence = sep.join(setofstrings)
sentence

sentence.upper()
sentence.lower()
sentence.capitalize()
sentence.title()
```

## Regular expressions

- Regular expressions are flexible string patterns that allow you to search for specific combinations of text
- Like "give me all the words that end in Y"
- It's so flexible, it's hard to learn (trial and error!)
- We will use the `stringr` package in tidyverse:
  - https://stringr.tidyverse.org/articles/regular-expressions.html
  - BUT there are some great base `R` functions as well: `grep`, `gsub`

## Regular expressions

- `.` matches a single character
- `^` matches the start of a string
- `$` matches the end of a string
- `*` matches zero or more cases of the previous character `b*` would match no or infinite letter `b`
- `?` matches zero or one of the previous previous character `b?` would match no or one b
- `+` matches one more cases of previous character `b+` would match one or infinite b

## Regular expressions

- `|` is the OR operator
- `[]` matches any character found in the brackets
- `[^...]` matches a character NOT present in the brackets after the `^`
- `\d` matches any decimal digits, can also use `[0-9]`
- `\D` matches any non-digits, can also use `[^0-9]`
- `\s` matches any white space character
- `\S` matches non-white space characters
- `\w` matches any alphanumeric characters, can also use `[a-zA-Z0-9_]`
- `\W` matches any non-alphanumeric characters, can also use `[^a-zA-Z0-9_]`

## Regular expressions

```{r}
##r chunk
sentence = "We can talk about numbers like how great is 5 or what is a ? doing here?"
str_extract(sentence, pattern = "5")
str_extract(sentence, pattern = "\\d")

str_extract_all(sentence, pattern = "\\?")

str_detect(sentence, pattern = "n")

str_replace_all(sentence, pattern = "\\?", replacement = "!")
```

```{python}
##python chunk
import re
sentence = "We can talk about numbers like how great is 5 or what is a ? doing here?"

#re.match - only finds the match at the beginning of the string
print(re.search("4", sentence))
print(re.search("\\d", sentence))
print(re.search("\\?", sentence)) #note only first one

print(re.findall("\\?", sentence))
print(re.finditer("\\?", sentence))

re.sub("\\?", "!", sentence)
```

## What do I need to do to clean up data?

- Remove weird symbols and HTML tags 
- Tokenize it 
- Remove unnecessary tokens and stopwords
- Contractions!
- Spelling errors
- ... then all the things you can do with that: stemming, lemmatization, tagging, chunking, and parsing
- Remember GIGO!

## Terminology

- This step is akin to data cleaning for statistical analysis
- Text preprocessing or normalization 
- Creates a standardized format
- Allows you to combine and/or compare tokens

## Removing noise

- Specially, let's do some simple web scraping and clean up that code. 
- We can use `rvest` to get html data and clean it up.

```{r}
##r chunk
library(rvest)
blog_url = "https://www.aggieerin.com/post/getting-translations-with-rvest-and-selenium/"
blog_post = read_html(blog_url)
clean_text = html_text(blog_post)

#forgot that you need to find all the instances, since the meta
#data has the introduction as information
str_locate_all(clean_text, "In this guide")
str_locate_all(clean_text, "Enjoy!")
clean_text <- substr(clean_text, 3873, 8202) 
clean_text
```

## Removing noise

- Use the `requests` package to pull html pages.
- Use `BeautifulSoup` to clean it up (most of the time).

```{python}
##python chunk
import requests
blog_post = requests.get("https://www.aggieerin.com/post/getting-translations-with-rvest-and-selenium/")
content = blog_post.content
print(content[1000:2000])
```

## Removing noise

```{python}
##python chunk
from bs4 import BeautifulSoup
clean_content = BeautifulSoup(content)
clean_text = clean_content.get_text()
#print(clean_text[:1000])
re.search("In this guide", clean_text)
clean_text = clean_text[495:]
print(clean_text)
```

## Tokenization 

- Tokenization is when you work on breaking down a long string into constituents. 
- Generally, this idea means breaking down text into individual words, but you might be interested in breaking things down into sentences, paragraphs, etc. 
- Remember, a token is usually considered an individual unit of meaning or word (and unique tokens are called types). 

## Sentence tokenization

- Sometimes this process is called sentence segmentation 
- The basic technique is to simply break things down based on a `.` or `!` or `\n` characters.
- We can use the `tokenizers` library in `R` to get us started. 

```{r}
##r chunk
library(tokenizers)
list_sentences <- unlist(tokenize_sentences(clean_text))
tokenize_sentences(clean_text)[[1]][3:8] ##give me just a few parts

count_sentences(clean_text) # hmmm
temp = unlist(tokenize_sentences(clean_text))
length(temp)
```

## Sentence tokenization

- `nltk` provides great tokenization options that are preprogrammed. 
- The default is the `PunktSentenceTokenizer` - which is a pretrained model to find abbreviations, collocations, and sentence boundaries. 
- Said to work well for European languages. 

```{python}
##python chunk
import nltk
sentences = nltk.sent_tokenize(clean_text)
print(sentences[1:3])
len(sentences)
```

## Sentence tokenization

- You can also use regular expressions to tokenize sentences
- I would only suggest this approach with difficult, strangely formatted text
- You could also supplement the text that has already been preprocessed with the regular tokenizers

## Word tokenization 

- Probably one of the most important components to NLP work 
- Feels like this should be easy because it's just a simple white space right?
- Don't forget about contractions! Spelling errors! And languages that are logographic.

## Word tokenization

```{r}
##r chunk
tokenize_words(clean_text,
               lowercase = T,
               stopwords = NULL, #more on this later
               strip_punct = T,
               strip_numeric = F,
               simplify = F) #list format

#tokenize_ptb(clean_text) Penn TreeBank option (see below)
```

## Word tokenization

- Functions in `nltk`:
  - word_tokenize
  - TreeBankTokenizer
  - TokTokTokenizer
  - RegexpTokenizer
- `spacy`!

## Word tokenization

- `word_tokenize` is a special instance of the Penn TreeBank Tokenizer 
- This tokenizer is a regular expression monster
  - Focuses on periods
  - Separates commas and single quotes when combined with a white space
  - Punctuation is included as a separate token
  - Deals with contractions (sort of)

```{python}
##python chunk
words = nltk.word_tokenize(clean_text)
print(words[50:60])
```

## Spacy

- https://spacy.io/usage/models

```{python}
##python chunk
import spacy

#this is very common naming to get spacy langauge models started
nlp = spacy.load('en_core_web_sm')

spacy_processed = nlp(clean_text)

list(spacy_processed.sents)[20:30]
len(list(spacy_processed.sents))
```

## Word tokenization

```{python}
##python chunk
print([word.text for word in spacy_processed][:500])
```

## Removing symbols

- Sometimes, things do not process correctly or the machine can't handle the accented characters such as `áö`. 
- We would want to normalize them to the language you are processing in. 
- The `iconv` base R function is also recommend, if you just want to strip them out.
- `stringi` appears to have a good replacement function. 

```{r}
##r chunk
characters = "éáö"

library(stringi)

stri_trans_general(str = characters,
                   id = "latin-ascii")
```

## Removing symbols

```{python}
##python chunk
import unicodedata

def remove_accented_chars(text):
  text = unicodedata.normalize('NFKD', text).encode('ascii', 'ignore').decode('utf-8', 'ignore')
  return text

remove_accented_chars(r.characters)
```

## Contractions

- Contractions are shortened or combined forms of several words
- Like "won't" is "will" and "not"
- They present issues in processing text because you have to account for all the different combinations
- The best way to deal with this problem is to have a look-up dictionary that maps the contraction to the expanded form 
- Good thing those exist already!
- You could make your own for special lexicons (like chat logs)

## Contractions

```{r}
##r chunk
library(textclean)

clean_text = str_replace_all(clean_text, 
                        pattern = "’", 
                        replacement = "'")

replace_contraction(clean_text, 
                    contraction.key = lexicon::key_contractions, #default
                    ignore.case = T) #default
```

## Contractions

```{r}
##r chunk
#py_install("contractions", pip = T)
```

```{python}
##python chunk
import contractions

contractions.fix(clean_text)

#from contractions import contractions_dict
#for contraction, expansion in contractions_dict.items():
#  clean_text = clean_text.replace(contraction, expansion)
```

## Correcting text

- We often have to deal with "incorrect" text:
  - Slang: heyyyyy
  - Spelling: hye 
  - Stemming versus lemmatization
  
## Repeated characters

Regex to the rescue!

```{r}
##r chunk
long_text = "finallllyyyyyy"
str_replace_all(long_text, pattern = "([[:alpha:]])\\1+", replacement = "\\1")
```

```{python}
##python chunk
long_text = "finallllyyyyyy"
re.sub(r"(\w)\1+",r"\1", long_text)
```

## Spelling

- Spelling options vary based on packages and options
- Definitely check what spelling options are being suggested!

```{r}
##r chunk
library(hunspell)

wordlist = c("thse", "wods", "mispelled")

# Spell check the words
spelling.errors <- hunspell(wordlist)
spelling.sugg <- hunspell_suggest(unique(unlist(spelling.errors)), dict = dictionary("en_US"))

# Pick the first suggestion
spelling.sugg <- unlist(lapply(spelling.sugg, function(x) x[1]))
spelling.dict <- as.data.frame(cbind(spelling.errors = unique(unlist(spelling.errors)),spelling.sugg))
spelling.dict$spelling.pattern <- paste0("\\b", spelling.dict$spelling.errors, "\\b")

#Replace the words 
stri_replace_all_regex(str = wordlist,
                       pattern = spelling.dict$spelling.pattern,
                       replacement = spelling.dict$spelling.sugg,
                       vectorize_all = FALSE)
```

## Spelling

```{r}
##r chunk
#py_install("textblob")
```

```{python}
##python chunk
from textblob import Word
wordlist = ["thse", "wods", "mispelled"]

[Word(word).correct() for word in wordlist]
```

## Stemming

- Remember, morphemes - which are the smallest unit of meaning 
- Stemming is a regex type process in which you simply "cut off" the stem or inflection of the words
- jumping, jumps, jumped --> jump because you just remove `ing`, `s`, and `ed`
- However, that means that wings --> w because the `s` and `ing` are removed
- Compare this procedure to lemmatization, which is using a dictionary to look up the part of speech of the word, which should correspond to a specific root word (or lemma)
  - The part of speech is necessary because of word ambiguity, so that wings is recognized as noun, which means do not remove `ing`.

## Stemming

```{r}
##r chunk
wordlist = c("wings", "jumped", "morning", "reading")
library(tm)
stemDocument(wordlist, language = "english")
```

```{python}
##python chunk
wordlist = ["wings", "jumped", "morning", "reading"]

from nltk.stem import PorterStemmer 
from nltk.stem import LancasterStemmer

ps = PorterStemmer()
ls = LancasterStemmer()

[ps.stem(word) for word in wordlist]
[ls.stem(word) for word in wordlist]
```

## Lemmatization

- The best way to lemmatize in R is certainly not the easiest - as it uses a part of speech mapper and dictionary look up with TreeTagger 
- We can probably get by with the simpler functions and check out: https://cran.r-project.org/web/packages/textstem/README.html for more information on using different dictionaries

```{r}
##r chunk
library(textstem)
lemmatize_words(wordlist)

sentence = "My system keeps crashing his crashed yesterday, ours crashes daily"
lemmatize_strings(sentence)
```

## Lemmatization

```{python}
##python chunk
##remember we imported spacy above
sentence = "My system keeps crashing his crashed yesterday, ours crashes daily"

def lemmatize_text(text):
  text = nlp(text)
  text = " ".join([word.lemma_ if word.lemma_ != "-PRON-" else word.text for word in text])
  return text

lemmatize_text(sentence)
```

## Stopwords

- Stopwords are the function words in a sentence like `the, an, a, of, but`
  - Compare this to the nouns, verbs, etc. that help portray meaning in a sentence
- We usually want to remove them as unnecessary for our analysis
- There are so many ways to do this in R it's mind boggling, favorite is probably `tm`

```{r}
##r chunk
head(tm::stopwords(kind = "SMART"))
removeWords(sentence, stopwords(kind = "SMART"))
```

## Stopwords

- Let's look at this complex loop exclusion
  - Give me words in the tokenized sentence, if those words are not in the stopword list 

```{python}
##python chunk
from nltk.corpus import stopwords

set(stopwords.words('english'))

[word for word in nltk.word_tokenize(sentence) if word not in stopwords.words('english')]
```

## Bring it all together

- There is no one "correct" normalization procedure
- You should examine the text at each step and determine if you have processed it appropriately
- You will change/update/work through the steps listed here based on the task at hand

## Summary

- In this lecture you learned:
  - Text is very messy, and we have to clean it up.
  - Slicing and calling parts of variables in each language
  - Tokenization
  - Regular expressions
  - Removing symbols
  - Contractions
  - Spelling and chat type issues (yaaaayyyy versus yay)
  - Stemming
  - Lemmatization
  - Stopwords
  - Bringing it all together 
- Next up: part of speech tagging




