---
title: 'Sentiment Analysis'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the libraries + functions


- Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly. 
- Import the separate python file that includes the functions you will need for the classification reports. 

```{r libaries}
##r chunk
```

- Load the Python libraries or functions that you will use for that section. 

```{python}
##python chunk

```

## The Data

- This dataset includes tweets that have been coded as either negative or positive. 
- Import the data using either R or Python. I put a Python chunk here because you will need one to import the data, but if you want to first import into R, that's fine. 

```{python}
##python chunk

```

## Clean up the data (text normalization)

- Use our clean text function from this lecture to clean the text for this analysis. 

```{python}
##python chunk

```

## TextBlob

- Calculate the expected polarity for all the tweets.
- Using a cut off score of 0, change the polarity numbers to positive and negative categories.
- Display the performance metrics of using Textblob on this dataset. 

```{python}
##python chunk

```

## AFINN

- Calculate the expected polarity for all the tweets using AFINN.
- Using a cut off score of 0, change the polarity numbers to positive and negative categories.
- Display the performance metrics of using AFINN on this dataset. 

```{python}
##python chunk

```

## Split the dataset

- Split the dataset into training and testing datasets. 

```{python}
##python chunk

```

## TF-IDF

- Calculate features for testing and training using the TF-IDF vectorizer.

```{python}
##python chunk

```

## Logistic Regression Classifier

- Create a blank logistic regression model.
- Fit the the model to the training data.
- Create the predicted value for the testing data.

```{python}
##python chunk

```

## Accuracy and Classification Report

- Display the performance metrics of the logistic regression model on the testing data.

```{python}
##python chunk

```

## Topic Model Positive Reviews

- Create a dataset of just the positive reviews. 
- Create a dictionary and document term matrix to start the topics model.

```{python}
##python chunk

```

## Topic Model

- Create the LDA Topic Model for the positive reviews with three topics.

```{python}
##python chunk

```

## Terms for the Topics

- Print out the top terms for each of the topics. 

```{python}
##python chunk

```

## Interpretation

- Which model best represented the polarity in the dataset? 
- Looking at the topics analysis, what are main positive components to the data? 