---
title: 'Part of Speech Tagging Assignment'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries / R Setup

- In this section, include the libraries you need for the *R* questions.  

```{r}
##r chunk
#devtools::install_github("bradleyboehmke/harrypotter")
library(harrypotter)

##pick one of the harrypotter books to analyze with your POS text
##https://github.com/bradleyboehmke/harrypotter check out the options
##load it using data(book title)

```

- In this section, include import functions to load the packages you will use for Python.
- Also transfer your `book_data` from R into Python.  

```{python}
##python chunk

```

## Tagger Package

- Use the `tagger` package to tag your chosen book and print out the first chapter only (i.e., row 1 of the book you chose). 
- Use something like `(book[1])[[1]][1:10]` to print out the first few tags. 
- Use the universal tag set and plot options to see what the most common parts of speech are for your chapter.
- What are the top two most common parts of speech? 

```{r}
##r chunk

```

## RDR POS Tagger

- Create an English language model that tags for part of speech.
- Tag your first book chapter for part of speech. 
- Use something like `head(...(book[1]))` to print out the first few examples. 

```{r}
##r chunk

```

## spaCy

- Import spacy and the English language module.
- Tag the first chapter of your book using spacy, and print out the results. 
- Use the `pandas` option at the beginning of the lecture to print out only a few rows. 

```{python}
##python chunk

```

## Training your own tagger

- Create a Default tagger in Python using `nltk`. 
- The default option should be "NN" for nouns.
- You do not have to use the tagger yet, just create it for a combined tagger to use later. (Don't tag! Don't print it out!)

```{python}
##python chunk

```

## Unigram Tagger 

- Create a unigram tagger that is trained on the entire Brown corpus with tagged sentences. 
  - Import the Brown corpus.
  - Split the data into test and train. 
  - Train your unigram tagger on the training sentences.
  - Use the default tagger you created above as the backoff. 
  - Do not use the tagger here, just train it. 

```{python}
##python chunk

```

## Evaluate

- Use the `.evaluate` function on your testing data to determine the accuracy of your tagger. 

```{python}
##python chunk

```

## Apply to Harry Potter

- Use the tagger you created above to apply to the first chapter of your Harry Potter book.
- Hint: save your book as only the first chapter and then transfer to python to help make this shorter. 
- Second hint: be sure to tokenize the data first!
- Use something like `tagger.tag(book)[1:10]` to print out only the first ten tags. 

```{python}
##python chunk

```

## Compare Results

- Examine the output from the different taggers we used to tag Harry Potter. 
- Are there any immediate differences you can notice when tagging?
- Which tagger seems like the easiest to apply?
- Why might the Brown corpus not be very good at tagging Harry Potter books? 