---
title: "WordNet and Entity Recognition"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: 
  slidy_presentation:
    increment: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Semantic Analysis

- Recap: we have now learned how to tag datasets for parts of speech and build your own POS tagger
- At the lowest level, this task is a small measure of semanticity - or being to understand meaning in a text
  - POS tells us a lot about meaning, even without knowing the literal meaning of the words we are tagging
- How might we get at the meaning of words?

## Semantic Analysis

- We will discuss how to explore WordNet and synsets
- Analyze lexical semantic relations
- Word sense disambiguation
- Named Entity Recognition

## WordNet

- A large lexical database - started in English and has been expanded to other languages 
- https://wordnet.princeton.edu/ 
- Remember that we discussed the difference between *function* and *content* words
- WordNet is mostly a dictionary of *content* words - nouns, adjectives, adverbs, and verbs
- WordNet has an hierarchical structure, wherein each item is related to every other item in a tree like fashion

## WordNet

- Words are clustered into synsets - or synonym sets - wherein these words are of the same semantic meaning
- Contains over 150,000 words grouped into 120,000(ish) synsets and many more word-sense pairs
- WordNet can be accessed through `nltk` in Python and the `wordnet` package in R

```{r}
##r chunk
#install.packages("wordnet")
library(reticulate)
py_config()
#py_install("nltk")
```

```{python echo = F}
import platform
if platform.system() == "Windows":
    import os
    os.environ[ 'MPLCONFIGDIR' ] = '/tmp/'
    os.environ['SCIKIT_LEARN_DATA'] = "C:/Users/EBuchanan.HU/py_stuff"
```

## Synsets

- These are defined as words that are semantically similar or synonyms
- They may not be exactly the same, but centered around the same content and concepts (i.e., they have similar features or relations to other words)
- These might also include collocations (multiword combinations) rather than just single words
- Additionally, words with multiple senses or meanings (polysemes) are noted and assigned to different synsets based on their various meanings

## Fruit in R

- WordNet in *R* is a bit complex.
  - First, define the type of filter you want to use.
  - Filters can be "ContainsFilter", "EndsWithFilter", "ExactMatchFilter", "RegexFilter", "SoundFilter", "StartsWithFilter", and "WildcardFilter".

```{r}
##r chunk
library(wordnet)
setDict("C:/Program Files (x86)/WordNet/2.1/dict") #if wordnet error
filter <- getTermFilter("ExactMatchFilter", #find this exact word
                        word = "fruit", #what the word is
                        ignoreCase = TRUE) #should I ignore case
```

## Fruit in R

- Next, you would define how you want to get the related terms.
  - The indices can be: "ADJECTIVE", "ADVERB", "NOUN", or "VERB"
- Last, you put in the filter. 

```{r}
##r chunk
terms <- getIndexTerms("NOUN", #what type of word you want it to be
                       5, #maximum number of results to return
                       filter) #the filter you previously defined
terms
```

## Fruit in R

```{r}
##r chunk
#we could use lapply here to pull more than one
fruit_sets <- lapply(terms, getSynsets)

fruit_sets
```

## Fruit in Python

- The Python version is easier - you can grab all the types at once!

```{python}
##python chunk
from nltk.corpus import wordnet as wn
import pandas as pd

fruit_sets_py = wn.synsets("fruit")
print(fruit_sets_py)
```

## Fruit in Python

- You can also convert to a dataframe a lot easier!

```{python}
##python chunk
pd.set_option('display.max_columns', None)
fruit_df = pd.DataFrame([
  {"Synset": each_synset, 
  "Part of Speech": each_synset.pos(), 
  "Definition": each_synset.definition(), 
  "Lemmas": each_synset.lemma_names(), 
  "Examples": each_synset.examples()} 
  for each_synset in fruit_sets_py])

fruit_df

fruit_df["Definition"]
```

## Lexical Semantic Relationships

- Text Entailment the directional relation between a text and hypothesis
- Text: A hurricane hit Peter's town.
- Hypothesis: Peter's town was damaged.
- How might we make a system that can recognize entailment?

## Entailments in Python

- Entailments are coded into Wordnet, which we can pull from the `synset` using the `.entailments()` function. 
- There may be more than one synset, but here we are just pulling the first one by using `[0]`.

```{python}
for action in ["walk", "eat", "digest"]:
  action_synset = wn.synsets(action, pos = "v")[0] #take just the first one
  print(action_synset, "-- entails -->", action_synset.entailments())
```

## Other types of relations

- Homonyms: same written form/pronunciation but different meanings
- Homographs: same written form, different pronunciation or meaning

```{python}
##python chunk
for synset in wn.synsets("bank"):
  print(synset.name(), " - ", synset.definition())
```

## Synonyms and Antonyms

- Synsets are for synonyms, words with similar meanings
- Antonyms are words with opposite meanings

```{python}
##python chunk
large_synset = wn.synsets("large")
large_synset[1] #grab large as an adjective

large_synset[1].lemmas()
large_synset[1].lemmas()[0].antonyms()
```

## Another example

```{python}
##python chunk
term = "rich"
term_synset = wn.synsets(term)[:3] #only the first three have connections

for each_synset in term_synset:
  term_l = each_synset.lemmas()[0]
  term_s = term_l.synset()
  term_a = term_l.antonyms()[0].synset()
  
  print("Synonym: ", term_s.name())
  print("Definition: ", term_s.definition())
  print("Antonym: ", term_a.name())
  print("Definition: ", term_a.definition())
  
```

## Hyponyms and Hypernyms

- Hypernyms: a superordinate name, more abstract (animal)
- Comparison word (dog)
- Hyponyms: a subordinate name, more specific (beagle)

```{python}
##python chunk
dog_synset = wn.synsets("dog")
dog_synset
dog = dog_synset[0]

dog.hypernyms()
dog.hyponyms()
```

## Why is this structure awesome?

- We can begin to track the hierarchical path of how words are connected to each other in meaning by tracking the paths of hyper/hyponyms. 

```{python}
##python
dog_paths = dog.hypernym_paths()
dog_paths
```

## Holonyms and Meronyms

- Holonyms are the name for a collection of objects

```{python}
##python chunk
tree_synset = wn.synsets("tree")
tree_synset
tree_synset[0].definition()
tree = tree_synset[0]
tree.member_holonyms()
```

## Holonyms and Meronyms

- Meronyms are the component parts of an object

```{python}
##python chunk
tree.part_meronyms()

tree.substance_meronyms()
```

## Similarity

- With the structure of the network, we can calculate similarity by finding the paths between words or the most common hypernym, etc.
- Let's look at an example:

```{python}
##python chunk
tree = wn.synsets("tree")
tree[0].definition()
tree = tree[0]

lion = wn.synsets("lion")
lion[0].definition()
lion = lion[0]

cat = wn.synsets("cat")
cat[0].definition()
cat = cat[0]
```

## Lowest common hypernyms

```{python}
##python chunk
tree.lowest_common_hypernyms(lion)
tree.lowest_common_hypernyms(cat)
lion.lowest_common_hypernyms(cat)

tree.path_similarity(lion)
tree.path_similarity(cat)
lion.path_similarity(cat)
```

## Other similarity measures

```{python}
##python chunk
from nltk.corpus import wordnet_ic
semcor_ic = wordnet_ic.ic('ic-semcor.dat')
tree.jcn_similarity(lion, semcor_ic)
lion.jcn_similarity(cat, semcor_ic)

tree.lin_similarity(lion, semcor_ic)
lion.lin_similarity(cat, semcor_ic)
```

## Word Sense Disambiguation

- We naturally use the context clues of a sentence to help us distinguish from different meanings possible in a word
- This task is useful for search enginges, keywords, etc. in a business context
- We can use the Lesk algorithm - examine the dictionary definition and the words around the target word in the sentence to see if they overlap.

```{python}
##python chunk 
from nltk.wsd import lesk
from nltk import word_tokenize

sample_text = [("The fruits on that plant have ripened", "n"),
          ("He finally reaped the fruit of his hard work as he won the race", "n")]

word = "fruit"
for sentence, pos_tag in sample_text:
  word_syn = lesk(word_tokenize(sentence.lower()), word, pos_tag)
  print("Sentence: ", sentence)
  print("Word Synset: ", word_syn)
  print("Corresponding Definition: ", word_syn.definition())
```

## One more example

```{python}
##python chunk 

sample_text = [("Lead is a very soft, malleable metal", "n"),
          ("John is the actor who plays the lead in that movie", "n"),
          ("This road leads to nowhere", "v")]

word = "lead"
for sentence, pos_tag in sample_text:
  word_syn = lesk(word_tokenize(sentence.lower()), word, pos_tag)
  print("Sentence: ", sentence)
  print("Word Synset: ", word_syn)
  print("Corresponding Definition: ", word_syn.definition())
```

## Named Entity Recognition

- Named entity - real-world object with a proper name
  - Much like the proper nouns that are tagged in part of speech tagging
  - Things like Twitter, France, and any celebrity
- GPE - geopolitical entity - like a country
- PER - person - like celebrities
- ORG - organization - like Twitter

## Categories and Labels

- How many categories can there be?
  - In part of speech tagging, we had a lot of different categories (50+ in Brown)
  - However, we could use the universal tag set and only have 10 tags
  - So it's up to us to determine the granularity of the tags

## Categories and Labels

- The most common tags are:
  - PER for person
  - LOC for location
  - ORG for organization
  - MISC for miscellaneous

## Categories and Labels

- Some other tags include:
  - NORP for nationalities, religious, political groups
  - FACILITY for buildings airports highways
  - GRE for countries
  - PRODUCT for objects, foods, etc. 
  - EVENT for hurricanes, battles, wars, sporting events
  - WORK_OF_ART for songs, books, paintings
  - LAW for named laws
  - LANGUAGE for languages 
  - Numbers: DATE, TIME, PERCENT, MONEY, QUANTITY, ORDINAL, CARDINAL
- Spacy uses about 18 different tags to be able to classify, which is what we are going to use 

## Why NER?

- Why should we use named entity recognition?
  - Entity linking is where we use NER to help us find relationships between things in a text.
  - *Rome is the capital of Italy.*
  - Rome and Italy would get tagged as a place (GPE) and then we could link them together. 
  - A business might use this ability to help identify links between organizations

## A note about generalization 

- One caveat with these models is that they are *brittle*
  - The training is specific to the task
  - Part of speech tagging can be fairly consistent across texts, as long as it's well trained
  - NER taggers will break more easily because they are trained to recognize specific contexts 

## Training models

- These models are trained in the same fashion as the part of speech tagging that we demonstrated in the last chapter 
  - Instead of datasets tagged with POS, we will be using datasets that are tagged with entities 
- What might we use to help classify these objects?
  - Obviously, we can have a look up dictionary of famous places, names, etc.
  - The limitation would be that this dictionary would be quite large, and you would miss new things that weren't programmed until it was updated.

## Training models

- What other things might we use?
  - Words around the target word
  - Prefixes or suffixes
  - Special symbols
  - Uppercase words 
- All of these are features we might use to help us train and build a model

## Training models

- After we figure out the features we want to use to categorize our named entities, the task becomes a machine learning classification task
- A popular algorithm is Conditional Random Fields and some deep learning methods

## How to Tag

- IOB tagging: creates *chunks* of text to help us do named entity recognition
- We often are interested in noun phrases, as named entities are often nouns
  - B: word tagged as the beginning of the chunk
  - I: words tagged as the inside of the chunk
  - O: word tagged as the outside of the chunk
- You need all three of these to mark the beginning and the end
- The I is necessary to make sure that each word is tagged so every entry has a code

## How to Tag

- Spacy also uses L and U tags and gives them slightly different names
  - B: beginning
  - I: inside
  - L: last (instead of outside)
  - U: unit, a single entity token 
  - O: a non-entity token
  
## The Stanford Named Entity Recognition Tagger

- A famous named entity recognition tagger that is available in nltk
- Written in java - so the set up requires finding the java files and having java set up correctly
- Is a conditional random field algorithm that uses pattern recognition to learn patterns

## NER with spacy

```{python}
##python chunk
import spacy
nlp = spacy.load("en_core_web_sm")

##process with nlp
example1 = nlp("Donald Trump visited the government headquarters in France today.")
example2 = nlp("He studies philosophy at Paris Nanterre University, completed a Master's of Public Affairs at Sciences Po, and graduate from the Ecole nationale d'administration (ENA) in 2004.")
```

## How to Automatically Detect Entities

- Notice how it tags the names and places.
- Also notice how there are empty spaces 

```{python}
##python chunk
for token in example1:
  print(token.text, token.ent_type_)
```

## How to Automatically Detect Entities

```{python}
##python chunk
for token in example2:
  print(token.text, token.ent_type_)
```

## How to Train your own NER Tagger

- To train models in spacy, you start with a blank model in a specific language. 
- Next add some information about the type of model you want to build
- Tutorial taken from: https://sematext.com/blog/entity-extraction-with-spacy/ and https://spacy.io/usage/training 

```{python}
##python chunk

#empty spacy model
nlp = spacy.blank("en")  

#add a name for training
nlp.vocab.vectors.name = 'example_model_training'   
```

## How to Train your own NER Tagger

- Spacy models are built on "pipes", so we will add a NER pipe 

```{python}
##python chunk
#add NER pipeline
ner = nlp.create_pipe('ner')  
#add pipeline to our blank model we created
nlp.add_pipe(ner, last=True)  
```

## How to Train your own NER Tagger

- Create some type of training data, here's a very small example. 
- Notice this is a list [] of tuples () that contain dictionaries {}. 
- The "u" indicates unicode. 

```{python}
##python chunk
# training data
training_data = [ #start our list

    ( #start a tuple
      #first is the text
      u"Search Analytics: Business Value & BigData NoSQL Backend, Otis Gospodnetic", 
      { #start a dictionary
        #first key is always entities
        #second value which is a LIST of TUPLES
        'entities': [ #start value list
          #slicing to find the specific section of the text
          #start number, end number, entity tag
          (58,74,'PERSON') 
          ] #end value list
        } #end dictionary 
    ), #end of the tuple 
    
  ( #start tuple 
    #text 
    u"Introduction to Elasticsearch by Radu", 
    { #start dictionary 
      'entities': [ #list for values
        (16,29,'TECH'), (33, 37, 'PERSON') 
      ] #end of list 
    } #end dictionary
  ) #end tuple

  ] #end list 
```

## How to Train your own NER Tagger

- We need to tell our model what type of tags to expect.

```{python}
##python chunk
nlp.entity.add_label('PERSON')
nlp.entity.add_label('TECH')
```

## How to Train your own NER Tagger

- Let's start training!

```{python}
##python chunk
#begin training
optimizer = nlp.begin_training()
import random

#run through training
for i in range(20):
    random.shuffle(training_data)
    for text, annotations in training_data:
        nlp.update([text], [annotations], sgd=optimizer)
```

## How to Train your own NER Tagger

- You can save your model for later.

```{python}
##python chunk
#save your model if you want to use it later
nlp.to_disk("./model")
```

## Using your NER Tagger 

```{python}
##python chunk
example3 = nlp(u"#bbuzz 2016: Otis Gospodnetic - Running High Performance And Fault Tolerant Elasticsearch ")

for entity in example3.ents:
  print(entity.label_, ' | ', entity.text)
```

## Summary

- We explored the idea of learning about meaning using Wordnet.
- With Wordnet, we can find related words and also calculate similarity.
- Similar to part of speech tagging, we can also create models that do named entity recognition.
- You learned how to set up a pipeline in spacy for building custom models. 
