---
title: "Chapter 6 Lab"
author: "Enter Yo Name"
date: "11/12/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

People are selfish, yet morally motivated. Morality is universal, yet culturally variable. Such apparent contradictions are dissolving as research from many disciplines converges on a few shared principles, including the importance of moral intuitions, the socially functional (rather than truth-seeking) nature of moral thinking, and the coevolution of moral minds with cultural practices and institutions that create diverse moral communities. I propose a fourth principle to guide future research: Morality is about more than harm and fairness. More research is needed on the collective and religious parts of the moral domain, such as loyalty, authority, and spiritual purity.

Participants were asked to take a morality survey, where they marked questions as "whether something is right or wrong" and how relevant the question was to moral judgment (1 = never, 10 = always). These questions were grouped into five categories: harm, fairness, ingroup, authority, and purity. Participants were also coded on their political views in a partially continuous scale as very liberal to very conservative.

*Citation:* Haidt, J. (2007). The new synthesis in moral psychology. Science, 316, 998-1002.

# Dataset:

    - Politics – coding of the participant political views (1=Democrat, 2=Republican)
    - Right_wrong – number of items marked wrong (low numbers indicate lower morality cues)
    - Ratings of how relevant to morality the question was (grouped by topic of question):
        -	Harm
        -	Fairness
        -	Ingroup
        -	Authority
        -	Purity

```{r starting}

```

# Scatterplots:

Create a scatter plot of right_wrong and fairness.

    a.	Be sure to check x/y axis labels and length.
    b.	What type of relationship do these two variables appear to have?

```{r plot1}

```

Create a scatter plot of harm and authority.

    a.	Include a linear line on the graph. 
    b.	Be sure to check x/y axis labels and length.
    c.	What type of relationship do these two variables appear to have?
    
```{r plot2}

```
    
Create a scatter plot of ingroup and purity, grouping by politics.

    a.	Include a linear line on the graph. 
    b.	Be sure to check x/y axis labels and length.
    c.	What type of relationship do these two variables appear to have for each group?
    
```{r plot3}

```
 
# Correlation tests 

Include a correlation test (cor.test) for right_wrong and one of the morality variables (your choice).

    a.	Include the Pearson output.
    b.	Include the Spearman output. 
    c.	Include the Kendall output. 
    d.	Was the correlation significant?
    e.	Which correlation was strongest?
    
```{r correl1}

```
    
Include a correlation of politics and right_wrong.
    
    a.	What type of correlation is this answer?
    b.	Was the correlation significant?
    c.	What is the interpretation for that correlation? 
    
```{r correl2}

```

Calculate the difference in correlations for Republicans and Democrats on right_wrong and harm variables.
    
    a.	Include the output from the test.
    b.	Is there a significant difference in their correlations?
    
```{r correl3}

```
    
Calculate the difference in correlations for fairness with purity and right_wrong with purity.
    
    a.	Include the output from the test up to Pearson’s test.
    b.	Is there a significant difference in their correlations?

```{r correl4}

```
    
Calculate the partial AND semipartial correlations for all variables, and include the output. 

```{r partials}

```