---
title: "Chapter 10 Lab"
author: "Enter Yo’ Name"
date: "10/8/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

#Abstract 
The current study examined self-objectification and hope in a sample of undergraduate men from a Midwestern university in the United States. Specifically, an online survey utilizing self-report measures examined the associations between body surveillance and body shame through the lenses of Objectification Theory and the Broaden and Build Theory of Positive Emotions. 

*Citation*: Cole, B. P., Davidson, M., & Gervais, S. J. (2013). Body surveillance and body shame in college men: Are men who self-objectify less hopeful?. Sex Roles, 69, 29-41. doi:10.1007/s11199-013-0282-3

# Dataset:
-	Body surveillance: participants were pre-screened on their body checking and grouped into (1) none/very little, (2) moderate, and (3) extreme checking levels.
-	Body shame: participants were given a questionnaire on their levels of body shame, where high levels indicate high shame.  Scale is an average score that ranges from 0 to 10 points.

```{r starting}

```

Run Levene’s test to determine if you’ve met the homogeneity assumption. You will have to run ez to get this analysis. 
    a.	Did you meet the homogeneity assumption? 
    b.	Why or why not?
    
```{r levenes}

```

Run the one-way ANOVA based on these results. You can refer to the code above if you meet the assumption.
    a.	Was the omnibus ANOVA test significant?
    
```{r anova}

```

Calculate the following effect sizes:
    a.	$\eta^2$ - fill in from the ez output.
    b.	$\omega^2$

```{r effect}


```

Run a post hoc independent t-test with a Bonferroni correction.  

```{r posthoc}

```

Include the effect sizes for each comparison. 

```{r effectsize}

```

Create a table of the post hoc and effect size values:

```{r table, results='asis'}
tableprint = matrix(NA, nrow = 3, ncol = 3)

##row 1
##fill in where it says NA with the values for the right comparison
##column 2 = p value from post hoc
##column 3 = d value from post hoc

##row 1
tableprint[1, ] = c("None to Moderate", NA, NA)

##row 2
tableprint[2, ] = c("None to Extreme", NA, NA)

##row 3
tableprint[3, ] = c("Moderate to Extreme", NA, NA)

kable(tableprint, 
      digits = 3,
      col.names = c("Comparison", 
                    "p-value", 
                    "d-value"))
```

Run a trend analysis.
    a.	Is there a significant trend?  
    b.	Which type?
    
```{r trend}

```
