---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

#bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r setup}
##install papaja special library
##you only have to do this part once
##comment it out when you are done
#devtools::install_github("crsh/papaja")

##load papaja
library(papaja)

##load MOTE for decimals
library(MOTE)

library(knitr)
```

Last week we covered how to pull numbers from chunks and report them outside the chunk - using MOTE's apa function. Turns out papaja has that function too! :)

Let's run an example from my class to demonstrate a couple new things today:

```{r anova}
##import the data
library(haven)
master = read_spss("c10 viagra.sav")

##run an ANOVA
library(ez)
##you must have a participant number for ezANOVA
master$partno = 1:nrow(master)
master$dose = as.factor(master$dose)
options(scipen = 999)

ezoutput = ezANOVA(data = master,
                   dv = libido,
                   between = dose,
                   wid = partno,
                   type = 3, 
                   detailed = T)

ezoutput

##running a one way anova - if Levene's Test is significant
aovoutput = oneway.test(libido ~ dose, data = master)

aovoutput

##normal LM type output
lmoutput = lm(libido ~ dose, data = master)

lmoutput

#apa_print(ezoutput)
apa_print(aovoutput)
apa_print(lmoutput)

```

#Printing when you can use papaja

We talked last week about the apa_print() function. You can use that with S3 and S4 class objects, meaning lm/aov type answers.
- You would use apa_print(SAVEDOUTPUT), so here that would be apa_print(aovoutput)
- Depending on what is in the output, depends on what you can get out of it. 

So we can print the F statistics from the one-way test with `r apa_print(aovoutput)$statistic`. However, that's not the best, since the *df* are missing. We can explore how to report manually below.

LM outputs work even better. You get lots of options! Mostly, we might consider doing something like this: `r apa_print(lmoutput)$full_result$modelfit`. 

#Printing when you can't use papaja

So, what can we do if we want to dynamically use our numbers but can't use apa_print? We can figure out how to pull the numbers we want. 

I can print the whole ANOVA table:

`r kable(ezoutput$ANOVA)`

I'd probably just want to report it APA style. Using my understanding of matrices, I can figure out how to get numbers out I want. 

df = `r ezoutput$ANOVA[2,2]; ezoutput$ANOVA[2,3]`

F = `r ezoutput$ANOVA[2,6]`

p = `r ezoutput$ANOVA[2,7]`

eta = `r ezoutput$ANOVA[2,9]`

Putting that all together, I can do: 
*F*(`r ezoutput$ANOVA[2,2]`, `r ezoutput$ANOVA[2,3]`) = `r apa(ezoutput$ANOVA[2,6],2,T)`, 
*p* = `r apa(ezoutput$ANOVA[2,7],3,F)`, $\eta^2$ = `r apa(ezoutput$ANOVA[2,9], 2, F)`.

(as an aside, you do not need Latex to print to word with the symbols, only PDF).

```{r post_hoc}
post = pairwise.t.test(master$libido,
                master$dose,
                p.adjust.method = "bonferroni", 
                paired = F, 
                var.equal = T)

post$p.value

post$p.value[1]; post$p.value[2]; post$p.value[3]; post$p.value[4]

post$p.value[1,1]; post$p.value[2,1]; post$p.value[1,2]; post$p.value[2,2]
```

#Printing use papaja's printnum and printp

We talked about the apa() function in the MOTE library last week. This week, let's cover printnum() and printp() in papaja. 

printnum works by:
- first, put in the number

- second, gt1 = T or F for greater than 1 (aka the leading zero issue)

- third, zero = T or F for if a number can be zero

- fourth, margin = 1 or 2 for matrices ... 1 for rows, 2 for columns, like the apply function

And a couple of other options, but these are the main ones. 

So for F = `r printnum(ezoutput$ANOVA[2,6])`, we can use the defaults because F can be greater than one and can also be zero.

But for eta = `r printnum(ezoutput$ANOVA[2,9], gt1 = F)`.

You can also use the digits command to get more or less digits: `r printnum(ezoutput$ANOVA[2,9], gt1 = F, digits = 3)`.

printp is a separate wrapper with a very handy function that prints the < symbol for numbers less than .001, and automatically assumes three decimals as per APA style.

`r printp(ezoutput$ANOVA[2,7])`

`r printp(.000001)`

#Printing post hoc information

Using that information - let's pull out the post hoc p-values to report.

I could say one versus two was not significant, *p* = `r printp(post$p.value[1])`, while one versus three was significant, *p* = `r printp(post$p.value[2])`, and finally two versus three was not significant, *p* = `r printp(post$p.value[4])`. We'd want to include effect sizes, which is what we covered last week, if you are interested in MOTE and how to report those values. 

#Printing a table
I've covered the kable function before for my SEM class, but let's cover apa_table() in this video. 

1) To manually make a table, first create a blank matrix to put your information in.
2) Fill in your table with information you want to print. 
3) Use apa_table!

```{r table, echo=FALSE, results='asis'}

tableprint = matrix(NA, nrow = 3, ncol = 4)

tableprint[1, ] = c("Row 1", 4, 2, 6)
tableprint[2, ] = c("Row 2", post$p.value[1], post$p.value[2], post$p.value[4])
tableprint[3, ] = c("Row 3", "MORE", "ROWS", "ETC.")

tableprint[1, 2:4] = printnum(as.numeric(tableprint[1, 2:4]))
tableprint[2, 2:4] = printp(as.numeric(tableprint[2, 2:4]))

apa_table(tableprint,
          caption = "This part goes at the top",
          note = "This part goes at the bottom.",
          align = c("l", "c", "c", "c"),
          col.names = c("Variable Name", "Column 2", "Column 3", "Column 4"))

```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
