---
title: 'Linear Regression'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import the Data

Import the data from the Dutch Lexicon Project `DLP_words.csv`. All materials are from here:
http://crr.ugent.be/programs-data/lexicon-projects

Variables we are going to use:
- `rt`: Response Latency to the Lexical Decision Task
- `subtlex.frequency`: The frequency of the word from the Dutch Subtitle Project.
- `length`: Length of the word.
- `POS`: part of speech.
- `bigram.freq`: Summed frequency of the bigrams in the word (the sum of each two-letter combination frequency). 

```{r importdata}

```

## Load the Libraries + Functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libraries}

```

## Clean Up Part of Speech

Update the part of speech variable so that the Nouns are the comparison category. Here's what the labels mean:

ADJ - Adjective
N - Noun
WW - Verbs

```{r pos}

```

## Deal with Non-Normality

Since we are using frequencies, we should consider the non-normality of frequency. 
- Include a histogram of the original `subtlex.frequency` column.
- Log-transform the `subtlex.frequency` column. 
- Include a histogram of `bigram.freq` - note that it does not appear extremely skewed. 

```{r nonnormal}

```

QUESTION: Interpret your results from these histograms. Should you use the regular frequency or the transformed frequency? Describe the histograms and interpret (i.e., more than a few words for answers here).
ANSWER:

## Create Your Linear Model

See if you can predict response latencies (DV) with the following IVs: subtitle frequency, length, POS, and bigram frequency. 

```{r lmrt}

```

## Interpret Your Model

### Overall Model 

QUESTION: Interpret your model in this step. Can you predict response latencies? Provide evidence the model is better than a random guess. 

- Is the overall model statistically significant?
- What is the practical importance of the overall model? 

ANSWER:

### Coefficients

QUESTION: Which coefficients are statistically significant? What do they suggest predicts response latency? (i.e., give the non-stats interpretation of the coefficients)
ANSWER:

Calculate the $pr^2$ values below:

```{r pr2}

```

QUESTION: Which coefficients appear to predict the most variance? 
ANSWER: 

What do the dummy coded POS values mean? Calculate the means of each group below to help you interpret:

```{r posmeans}

```

QUESTION: Interpret the dummy coded results.
ANSWER: 

## Diagnostic Tests

### Outliers

Create an influence plot of the model using the `car` library. 

```{r influence}

```

QUESTION: Which data points appear to have the most influence on the model?
ANSWER: 

### Additivity

- Show that the correlations between predictors is less than .9.
- Show the VIF values. 

```{r additivity_vif}

```

QUESTION: Do we have additivity in our model? Explain how the VIF and correlation values support your answer. 
ANSWER: 

### Linearity

Include a diagnostic plot for linearity. 

```{r qqplot}

```

QUESTION: Does the data/model meet the linearity assumption? Explain how you came to this conclusion. 
ANSWER: 

### Normality 

Include a diagnostic plot for normality of the residuals. 

```{r normal}

```

QUESTION: Does the data/model meet the normality assumption? Explain how you came to this conclusion. 
ANSWER: 

### Homoscedasticity/Homogeneity

Include a diagnostic plot for homoscedasticity. 

```{r homogs}

```

QUESTION: Does the data/model meet the homoscedasticity assumption? Explain how you came to this conclusion. 
ANSWER: 


### Bootstrapping 

Use the function provided from class (included below) and the `boot` library to bootstrap the model you created 1000 times. 
- Include the estimates of the coefficients from the bootstrapping.
- Include the confidence intervals for at least one of the predictors (not the intercept).

Use the following to randomly sample 500 rows of data - generally, you have to have more bootstraps than rows of data, so this code will speed up your assignment. In the `boot` function use: `data = DF[sample(1:nrow(DF), 500, replace=FALSE),]` for the data argument changing DF to the name of your data frame.

```{r boot}
bootcoef <- function(formula, data, indices){
  d = data[indices, ] #randomize the data by row
  model = lm(formula, data = d) #run our model
  return(coef(model)) #give back coefficients
}
```

QUESTION: Interpret the results of the bootstrapping. Do you get similiar results to the overall model when sampling a smaller set? 
ANSWER: 




