---
title: 'Executive 2: Visualizations for Final Report'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Be sure to list the group members at the top! This assignment is the first component for your class project. Be sure all group members contribute, *and* each group member must submit the assignment individually. 

You can use either *R* or Python or both for this assignment. You should use the code and packages we used in class assignments, but these can be a mix and match of each computing language. You will add the appropriate type of code chunk for each section depending on the language you pick for that section. 

## Libraries / R Setup

- In this section, include the libraries you need for the *R* questions.  

```{r}
##r chunk

```

- In this section, include import functions to load the packages you will use for Python.

```{python}
##python chunk

```

## Import Subtitles

In this section, import your cleaned up subtitles from the last assignment. 

## Visualization

Create two visualizations of your data using the notes provided today. You should create two different types (word cloud, network chart, lexical dispersion, frequency). You will use these to supplement your final report! 