---
title: 'Entity Recognition + Parsing Assignment'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Be sure to list the group members at the top! This assignment is the first component for your class project. Be sure all group members contribute, *and* each group member must submit the assignment individually. 

You can use either *R* or Python or both for this assignment. You should use the code and packages we used in class assignments, but these can be a mix and match of each computing language. You will add the appropriate type of code chunk for each section depending on the language you pick for that section. 

## Libraries / R Setup

- In this section, include the libraries you need for the *R* questions.  

```{r}
##r chunk

```

- In this section, include import functions to load the packages you will use for Python.

```{python}
##python chunk

```

## Import Subtitles

- Import your subtitle data for the movie or TV show that you selected in the course proposal - use the clean version from the previous assignment.

## Definitions

- Pick three of your most popular nouns or verbs from your previous assignment. These words would most likely be tied to the theme of your movie/tv show. Use WordNET import the synsets for those terms. 
- How many different definitions do these terms have? 
- Can you find the definition that appears to match the one from your text? 
- Find one of the sentences that use one of your noun or verbs. Using the `lesk` algorithm, can you identify the right definition for that word? 

## Entity Recognition

- Use `spacy`'s default model to tag your subtitles with entities. 
- Save these entities into a dataframe or list.
- Calculate the most common types of entities found in your text. 
- Do any of the entities tagged surprise you? 

## Parsing

- Use `spacy` process the dependencies in your subtitles or tv show. 
- Pick two words (characters/nouns/verbs) from your most popular list from the first assign. Examine the child dependencies for these words.
- What do the dependencies tell you about the concepts you picked? How are these words discussed in the movie/tv show? What information can you use to understand what is happening in the show without watching it? 

## Interpretation

- Using parsing and entity recognition, we could begin to build a map of the characters and their relationships in the text. What other information could you use from these two techniques to help describe your text using code? 