---
title: 'Assignment 4: DCA'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create the Data

Is there a difference in twitter word usage of Donald Trump during his run for president versus while he is president?

- Data from: http://trumptwitterarchive.com/
- Not Prez data is Jan 2015 to Jan 2017
- Prez data is from Jan 2017 to Jan 2019
- Install `tokenizers` package, if you do not have it. 

```{r create_tweets}
master = read.csv("trump_tweets.csv", stringsAsFactors = F)
master = na.omit(master)

colnames(master)[1] = "time"

prez = subset(master, time == "prez")
notprez = subset(master, time == "not prez")

ptemp = tokenizers::tokenize_ngrams(as.character(prez$text),
                            lowercase = T,
                            n = 2)
pdata = as.data.frame(table(unlist(ptemp)))

nptemp = tokenizers::tokenize_ngrams(as.character(notprez$text),
                            lowercase = T,
                            n = 2)
npdata = as.data.frame(table(unlist(nptemp)))

final_data = merge(pdata, npdata, by = "Var1", all = TRUE)

colnames(final_data) = c("Bigram", "Prez", "NotPrez")
```

## Load the Libraries + Functions

Load all the libraries or functions that you will use to for the rest of the assignment. It is helpful to define your libraries and functions at the top of a report, so that others can know what they need for the report to compile correctly.

```{r libraries}

```


## Deal with NA values

Remember that the NA values just represent options that didn't occur in one time point versus the other. Fill those NA values in with zero. 

```{r updatezeros}

```

## Pick your construction

- Pick a construction to consider, remembering that the data has been put into bigrams (although you can change this to larger numbers above if you want).
- You can look for a particular word in a construction using regular expressions and the `grep` function. 
  - the `^` indicates that it should be the start of the bigram. 
  - the `$` indicates that it should be the last word of the bigram.
  - I recommend putting a space so you only get that particular word. 
  - You might consider using the word `make` - so the firstword would be "^make " or the lastword would be " make$". 

```{r reducedata}
firstword = "^word "
lastword = " word$"

#change to either first or last word here 
reduced_data = final_data[grep(firstword, final_data$Bigram), ]
```

## Summarize the data

Using Not Prez as `a` and Prez as `b`, create the vectors for a, b, c, and d.

```{r createabcd}

```

## Calculate aExp

Calculate the expected value of a for each bigram. 

```{r aExp}

```

## logPF

Calculate the log p-values from the Fisher test. 

```{r logpf}

```

## Calculate the top scores

Create the top 10 bigrams for Not Prez (positive scores) and for Prez (negative scores).

```{r combine}

```

## Interpreting the numbers

What can you gather from the different top scores for Not Prez and Prez? Did he appear to change his style once inaugurated? 
