---
title: "11 MGCFA"
author: "erin buchanan"
date: "09/18/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MGCFA Class Assignment

## Using the RS14 dataset, program the different models of a multigroup analysis using ethnicity as the grouping variable. 
    Use race_test as the variable:
        1 = Black
        2 = White 
    Be sure to first change the variable to a factor with labels. 
    
```{r import_data}
master <- read.csv("./11 mgcfa.csv")
head(master)
table(master$race_test)

master$race_test <- factor(master$race_test,
                           levels = c(1,2),
                           labels = c("Black", "White"))

table(master$race_test, useNA = "ifany")

master <- subset(master,
                 !is.na(race_test))
```

## Overall Model

```{r overallmodel}
overall.model <- 'RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14'

overall.fit <- cfa(model = overall.model,
                   data = master,
                   meanstructure = TRUE)

summary(overall.fit)
```

## Measurement Invariance

```{r}
library(equaltestMI)

MG.fit <- eqMI.main(model = overall.model, 
                    data = master,
                    group = "race_test",
                    meanstructure = TRUE,
                    output = "both", #mean, covariance, both  
                    equivalence.test = FALSE, #change this in a moment
                    adjRMSEA = TRUE, #but see new paper
                    projection = TRUE, #see notes
                    bootstrap = FALSE,
                    quiet = TRUE)
```

## Get Individual Groups

```{r}
table(master$race_test)
summary(MG.fit$convention.sem$LavaanOut$fit.configural.g1)
summary(MG.fit$convention.sem$LavaanOut$fit.configural.g2)
summary(MG.fit$convention.sem$LavaanOut$fit.combine.groups)
summary(MG.fit$convention.sem$LavaanOut$fit.metric)
summary(MG.fit$convention.sem$LavaanOut$fit.scalar)
summary(MG.fit$convention.sem$LavaanOut$fit.strict.residuals)
```

    Add partial invariance to your table if necessary by adding a new row. 
    
```{r table}
library(knitr)
tableprint = matrix(NA, nrow = 10, ncol = 8)
colnames(tableprint) = c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI", "Change CFI", "Different?")
##replace the 1:5 or 1:7 with the appropriate numbers
tableprint[1, ] = c("All Groups", 
                    fitmeasures(overall.fit, c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), "na", "na")
tableprint[2, ] = c("White", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.configural.g2, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), "na", "na")
tableprint[3, ] = c("Black", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.configural.g1, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), "na", "na")
tableprint[4, ] = c("Configural Invariance", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.combine.groups, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), "na", "na")
tableprint[5, ] = c("Metric Invariance", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.combine.groups, "cfi") - 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, "cfi"), "Invariant")
tableprint[6, ] = c("Scalar Invariance", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, "cfi") - 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi"), "Not Invariant")
tableprint[7, ] = c("Strict Invariance", fitmeasures(MG.fit$convention.sem$LavaanOut$fit.strict.residuals, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi") - 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), "Not Invariant")

kable(tableprint)
```

## What is the CFI you are trying to get to (i.e. CFI - .01)? 

0.91172420938273 - .01 = 0.9017242

## What questions would you freely estimate to get to partial invariance? 

```{r}
##write out partial codes
partial_syntax <- paste(colnames(master)[4:17], "~1") 

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = master,
              meanstructure = TRUE,
              group = "race_test",
              group.equal = c("loadings", "intercepts"),
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list

options(scipen = 999)
sort(CFI_list - fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi"), decreasing = T)
```

RS4!

```{r}
MG.fit_2 <- eqMI.main(model = overall.model, 
                    data = master,
                    group = "race_test",
                    meanstructure = TRUE,
                    group.partial = "RS4~1",
                    output = "both", #mean, covariance, both  
                    equivalence.test = FALSE, #change this in a moment
                    adjRMSEA = TRUE, #but see new paper
                    projection = TRUE, #see notes
                    bootstrap = FALSE,
                    quiet = TRUE)

tableprint[8, ] = c("Partial Scalar Invariance RS4", fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.scalar, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, "cfi") - 
                    fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.scalar, "cfi"), "Invariant")

tableprint[9, ] = c("Strict Invariance RS4", fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.scalar, "cfi") - 
                    fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), "Not Invariant")
```

```{r}
##write out partial codes
partial_syntax <- paste(colnames(master)[4:17], "~~", colnames(master)[4:17]) 

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = master,
              meanstructure = TRUE,
              group = "race_test",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = c("RS4~1", partial_syntax[i]))
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list

options(scipen = 999)
sort(CFI_list - fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), decreasing = T)
```

So we are going to release RS3 as the residuals 

```{r}
MG.fit_3 <- eqMI.main(model = overall.model, 
                    data = master,
                    group = "race_test",
                    meanstructure = TRUE,
                    group.partial = c("RS4~1", "RS3~~RS3"),
                    output = "both", #mean, covariance, both  
                    equivalence.test = FALSE, #change this in a moment
                    adjRMSEA = TRUE, #but see new paper
                    projection = TRUE, #see notes
                    bootstrap = FALSE,
                    quiet = TRUE)

tableprint[10, ] = c("Strict Invariance RS4 Intercept + RS3 Residual", fitmeasures(MG.fit_3$convention.sem$LavaanOut$fit.strict.residuals, 
                                          c("chisq", "df", "rmsea", 
                                               "srmr", "cfi")), 
                    fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.scalar, "cfi") - 
                    fitmeasures(MG.fit_3$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), "Not Invariant")

kable(tableprint)
```

## Interpret your findings - are the groups invariant?  Did you see a break down between groups anywhere? What does that break down imply?

Yes - intercept for RS4 is not invariant (it's different), and then the residual for RS3 is also different.

```{r}
summary(MG.fit_3$convention.sem$LavaanOut$fit.strict.residuals,
        standardized = T, 
        rsquare = T, 
        fit.measures = T)
```

For RS4 (friends), Blacks are rating this higher than Whites on average. For RS3 (stride), Blacks answers are twice as variable than Whites. 






