---
title: "12 MGCFA 2"
author: "erin buchanan"
date: "09/18/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lavaan)
```

## MGCFA Class Assignment
Program a multigroup model and calculate latent means. 
    DASS - Depression, Anxiety, and Stress Scale
        Depression: Questions 3, 5, 10, 13, 16, 17, 21
        Anxiety: Questions 2, 4, 7, 9, 15, 19, 20
        Stress: 1, 6, 8, 11, 12, 14, 18

    Test gender as the grouping variable:
        1 = female
        2 = male 

```{r}
master <- read.csv("../12 mgcfa.csv")
head(master)

table(master$gender, useNA = "ifany")
```

```{r}
overall.model <- 'depression =~ Q3 + Q5 + Q10 + Q13 + Q16 + Q17 + Q21
anxiety =~ Q2 + Q4 + Q7 + Q9 + Q15 + Q19 + Q20
stress =~ Q1 + Q6 + Q8 + Q11 + Q12 + Q14 + Q18'

master2 = master[ sample(nrow(master), size = 1500, replace = T), ]
overall.model <- 'depression =~ Q3 + Q5 + Q10 + Q13 + Q16 + Q17 + Q21 + Q2 + Q4 + Q7 + Q9 + Q15 + Q19 + Q20 + Q1 + Q6 + Q8 + Q11 + Q12 + Q14 + Q18'
overall.fit <- cfa(model = overall.model,
                   data = master,
                   meanstructure = TRUE,
                   ordered = T)

summary(overall.fit,
        standardized = T,
        fit.measures = T,
        rsquare = T)
```

```{r}
library(equaltestMI)

MG.fit <- eqMI.main(model = overall.model, 
                    data = master,
                    group = "gender",
                    meanstructure = TRUE,
                    output = "both", #mean, covariance, both  
                    equivalence.test = FALSE, #change this in a moment
                    adjRMSEA = TRUE, #but see new paper
                    projection = TRUE, #see notes
                    bootstrap = FALSE,
                    quiet = TRUE)

summary(MG.fit$convention.sem$LavaanOut$fit.configural.g1)
summary(MG.fit$convention.sem$LavaanOut$fit.configural.g2)
summary(MG.fit$convention.sem$LavaanOut$fit.combine.groups)
summary(MG.fit$convention.sem$LavaanOut$fit.metric)
summary(MG.fit$convention.sem$LavaanOut$fit.scalar)
summary(MG.fit$convention.sem$LavaanOut$fit.strict.residuals)
```

## Create a table of the fit estimates. 

Add partial invariance to your table when necessary. 

```{r table}
library(knitr)
tableprint = matrix(NA, nrow = 8, ncol = 8)
colnames(tableprint) = c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI", "Change CFI", "Different?")
##replace the 1:5 or 1:7 with the appropriate numbers
tableprint[1, ] = c("All Groups", 
                    fitmeasures(overall.fit, c("chisq", "df", 
                                               "rmsea", "srmr", "cfi")), 
                    "na", "na")

tableprint[2, ] = c("Female", 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.configural.g1, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")), "na", "na")
tableprint[3, ] = c("Male", 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.configural.g2, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")),
                    "na", "na")
tableprint[4, ] = c("Configural Invariance", 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.combine.groups, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")),
                    "na", "na")
tableprint[5, ] = c("Metric Invariance",
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.combine.groups, "cfi") - 
                       fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, "cfi"), 
                    "Invariant")
tableprint[6, ] = c("Scalar Invariance", 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.metric, "cfi") - 
                       fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi"), 
                    "Invariant")
tableprint[7, ] = c("Strict Invariance", 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.strict.residuals, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi") - 
                       fitmeasures(MG.fit$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), 
                    "Not Invariant")
kable(tableprint)
```

```{r}
##write out partial codes
partial_syntax <- paste(colnames(master)[3:23], "~~", colnames(master)[3:23]) 

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = master,
              meanstructure = TRUE,
              group = "gender",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list

options(scipen = 999)
sort(CFI_list - fitmeasures(MG.fit$convention.sem$LavaanOut$fit.strict.residuals, ##model you are trying to fix 
                            "cfi"), decreasing = T)
```

```{r}
MG.fit_2 <- eqMI.main(model = overall.model, 
                    data = master,
                    group = "gender",
                    meanstructure = TRUE,
                    group.partial = "Q11 ~~ Q11",
                    output = "both", #mean, covariance, both  
                    equivalence.test = FALSE, #change this in a moment
                    adjRMSEA = TRUE, #but see new paper
                    projection = TRUE, #see notes
                    bootstrap = FALSE,
                    quiet = TRUE)

tableprint[8, ] = c("Partial Strict Invariance Q11", 
                    fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals, 
                                c("chisq", "df", "rmsea", "srmr", "cfi")), 
                    fitmeasures(MG.fit$convention.sem$LavaanOut$fit.scalar, "cfi") - 
                       fitmeasures(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), 
                    "Invariant")
```

## What pieces would you freely estimate to get to partial invariance? 

Q11 residuals 

## Interpret your findings - are the groups invariant?  Did you see a break down between groups anywhere? What does that break down imply?

```{r}
summary(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals)
```

For q11, females have twice the variance than males. 

## Include the latent means and standard deviations for your groups.

```{r}
predicted_scores <- lavPredict(MG.fit_2$convention.sem$LavaanOut$fit.strict.residuals,
                               type = "ov")

predicted_scores <- as.data.frame(do.call(rbind, predicted_scores))

table(master$gender)

predicted_scores$gender <- c(rep("Female", 246), rep("Male", 165))

predicted_scores$depression <- apply(predicted_scores[ , 1:7], 1, sum)
predicted_scores$anxiety <- apply(predicted_scores[ , 8:14], 1, sum)
predicted_scores$stress <- apply(predicted_scores[ , 15:21], 1, sum)

tapply(predicted_scores$depression, predicted_scores$gender, mean)
tapply(predicted_scores$depression, predicted_scores$gender, sd)

tapply(predicted_scores$anxiety, predicted_scores$gender, mean)
tapply(predicted_scores$anxiety, predicted_scores$gender, sd)

tapply(predicted_scores$stress, predicted_scores$gender, mean)
tapply(predicted_scores$stress, predicted_scores$gender, sd)
```

## Use a t-test to determine if they are significantly different. Include Cohen's d for your test. 

```{r}
library(MOTE)

M_dep <- tapply(predicted_scores$depression, predicted_scores$gender, mean)
SD_dep <- tapply(predicted_scores$depression, predicted_scores$gender, sd)
N_dep <- tapply(predicted_scores$depression, predicted_scores$gender, length)

d.ind.t(M_dep[1], M_dep[2], SD_dep[1], SD_dep[2], N_dep[1], N_dep[2], a = .05)
```

```{r}
MG.fit_2$projection.res$projection$latent.test
```


