---
title: "1 Intro R"
author: "erin buchanan"
date: "6/11/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create R chunks to display both the output and code in this file. For each of the following sections, create the code to answer the question and output the answer (if necessary).

#	Make a vector of numbers. 
    o	Use the rep or seq function.
    o	Include a concatenate c().
```{r part 1}
vect = c(1,2,3,4)
vect
```


#	Use the length() function to figure out how long your vector is.

#	Make a matrix at least 5 by 5. 
    o	Pull out the value for row 2 column 3.

#	Use the head() function to look at the dataset USArrests. 
    o	Calculate a summary of USArrests.

#	Import a data set (attached). 
    o	Recode all the values to LEFT and RIGHT in the whichhand column.
    o	Create a summary of the dataset.
    o	Exclude all navalues in the dataset.
    o	Create a dataset with only LEFT handed participants.
    o	Calculate the correlation table of just the following variables: LR_switch, finger_switch, rha, word_length, letter_freq

#	Bonus: 
    o	Run a regression using the following: lm(rating~finger_switch, data=data) **or whatever you called the data
    o	Save the output of the regression.
    o	Pull out only the slope from the coefficients.