---
title: "10 MTMM"
author: "erin buchanan"
date: "6/26/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MTMM Class Assignment
## Program the steps of MTMM and include the fit indices, loadings, and an interpretation of the results from your analysis. 
    Traits:
        Meaning: 
            o	MLQ 1, 2, 5, 10
            o	SONG 1, 9
            o	PIL 4, 17
        Purpose:
            o	MLQ 3, 4, 6, 8, 9
            o	SONG 2, 8 
            o	PIL 3, 20 
    Methods:
        o	MLQ
        o	PIL
        o	SONG

## Create a table of the models, using the starting point below:
```{r model table}
library(knitr)
tableprint = matrix(NA, nrow = 4, ncol = 6)
colnames(tableprint) = c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI")
##replace the 1:5 with the appropriate numbers
tableprint[1, ] = c("Model 1 - Correlated traits and methods", 1:5)
tableprint[2, ] = c("Model 2 - No traits, correlated methods", 1:5)
tableprint[3, ] = c("Model 3 - Perfectly correlated traits, correlated methods", 1:5)
tableprint[4, ] = c("Model 4 - Correlated traits, uncorrelated methods", 1:5)

kable(tableprint)
```

## Create a model comparison table, using the starting point below:

```{r comparison model}
library(knitr)
tableprint = matrix(NA, nrow = 3, ncol = 6)
colnames(tableprint) = c("Model", "Change Chi-Square", "Change df", 
                         "Critical Chi-Square", "Change CFI", "Significant Change")
##replace the 1:5 with the appropriate numbers
tableprint[1, ] = c("Convergent Validity Traits Model 1 - 2", 1:5)
tableprint[2, ] = c("Discriminant Validity Traits Model 1 - 3", 1:5)
tableprint[3, ] = c("Discriminant Validity Methods Model 1 - 4", 1:5)

kable(tableprint)

```

## Create a table of the estimates, using the starting point below: 

```{r estimates table}
library(knitr)
tableprint = matrix(NA, nrow = 17, ncol = 6)
colnames(tableprint) = c("Estimate", "Meaning", "Purpose", 
                         "MLQ", "PIL", "SONG")
##replace the 0 values with numbers, X values are marked off on purpose. 
tableprint[1, ] = c("MLQ 1", 0, "X", 0, "X", "X")
tableprint[2, ] = c("MLQ 2", 0, "X", 0, "X", "X")
tableprint[3, ] = c("MLQ 5", 0, "X", 0, "X", "X")
tableprint[4, ] = c("MLQ 10", 0, "X", 0, "X", "X")
tableprint[5, ] = c("PIL 4", 0, "X", "X", 0, "X")
tableprint[6, ] = c("PIL 17", 0, "X", "X", 0, "X")
tableprint[7, ] = c("SONG 1", 0, "X", "X", "X", 0)
tableprint[8, ] = c("SONG 9", 0, "X", "X", "X", 0)
tableprint[9, ] = c("MLQ 3", "X", 0, 0, "X", "X")
tableprint[10, ] = c("MLQ 4", "X", 0, 0, "X", "X")
tableprint[11, ] = c("MLQ 6", "X", 0, 0, "X", "X")
tableprint[12, ] = c("MLQ 8", "X", 0, 0, "X", "X")
tableprint[13, ] = c("MLQ 9", "X", 0, 0, "X", "X")
tableprint[14, ] = c("PIL 3", "X", 0, "X", 0, "X")
tableprint[15, ] = c("PIL 20", "X", 0, "X", 0, "X")
tableprint[16, ] = c("SONG 2", "X", 0, "X", "X", 0)
tableprint[17, ] = c("SONG 8", "X", 0, "X", "X", 0)


kable(tableprint)

```

## Correlations
    Traits correlations:
        Purpose to meaning:
    Methods correlations:
        PIL to MLQ: 
        PIL to SONG:
        MLQ to SONG:

## Interpret your results - explaining convergent and discriminant validity in context of the models and parameter estimates. 
