---
title: "11 MGCFA"
author: "erin buchanan"
date: "6/26/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MGCFA Class Assignment

## Using the RS14 dataset, program the different models of a multigroup analysis using ethnicity as the grouping variable. 
    Use race_test as the variable:
        1 = Black
        2 = White 
    Be sure to first change the variable to a factor with labels. 
    Add partial invariance to your table if necessary by adding a new row. 
```{r table}
library(knitr)
tableprint = matrix(NA, nrow = 7, ncol = 8)
colnames(tableprint) = c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI", "Change CFI", "Different?")
##replace the 1:5 or 1:7 with the appropriate numbers
tableprint[1, ] = c("All Groups", 1:5, "na", "na")
tableprint[2, ] = c("White", 1:5, "na", "na")
tableprint[3, ] = c("Black", 1:5, "na", "na")
tableprint[4, ] = c("Configural Invariance", 1:5, "na", "na")
tableprint[5, ] = c("Metric Invariance", 1:7)
tableprint[6, ] = c("Scalar Invariance", 1:7)
tableprint[7, ] = c("Strict Invariance", 1:7)

kable(tableprint)

```

## What is the CFI you are trying to get to (i.e. CFI - .01)? 

## What questions would you freely estimate to get to partial invariance? 

## Interpret your findings - are the groups invariant?  Did you see a break down between groups anywhere? What does that break down imply?
