---
title: "12 MGCFA 2"
author: "erin buchanan"
date: "6/26/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MGCFA Class Assignment
Program a multigroup model and calculate latent means. 
    DASS - Depression, Anxiety, and Stress Scale
        Depression: Questions 3, 5, 10, 13, 16, 17, 21
        Anxiety: Questions 2, 4, 7, 9, 15, 19, 20
        Stress: 1, 6, 8, 11, 12, 14, 18

    Test gender as the grouping variable:
        1 = female
        2 = male 

## Create a table of the fit estimates. 
Add partial invariance to your table when necessary. 

```{r table}
library(knitr)
tableprint = matrix(NA, nrow = 7, ncol = 8)
colnames(tableprint) = c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI", "Change CFI", "Different?")
##replace the 1:5 or 1:7 with the appropriate numbers
tableprint[1, ] = c("All Groups", 1:5, "na", "na")
tableprint[2, ] = c("Female", 1:5, "na", "na")
tableprint[3, ] = c("Male", 1:5, "na", "na")
tableprint[4, ] = c("Configural Invariance", 1:5, "na", "na")
tableprint[5, ] = c("Metric Invariance", 1:7)
tableprint[6, ] = c("Scalar Invariance", 1:7)
tableprint[7, ] = c("Strict Invariance", 1:7)

kable(tableprint)

```

## What pieces would you freely estimate to get to partial invariance? 

## Interpret your findings - are the groups invariant?  Did you see a break down between groups anywhere? What does that break down imply?

## Include the latent means and standard deviations for your groups.

## Use a t-test to determine if they are significantly different. Include Cohen's d for your test. 
You can use MOTE or you can use the cohen.d function. 
