---
title: "13 LCM"
author: "erin buchanan"
date: "6/26/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Latent Curve Class Assignment

Examine the following data for latent curve modeling. Participants were given a task to read a paragraph while hooked up to a biopac that measured heart rate. Each heart rate was subtracted from baseline. Here's the covariance table for five time points. 

```{r data}
##load the data
library(lavaan)
heart.cov = lav_matrix_lower2full(
  c(
  3.59,				
  3.11,	3.10,			
  2.91,	2.80,	2.82,		
  3.22,	3.05,	2.86,	3.30,	
  2.88,	2.63,	2.62,	2.82,	2.71)
  )

heart.mean = c(11.97,	11.72,	12.03,	11.96,	12.10)
```

## Create a table of the fit indices.
```{r fit indices}
library(knitr)
tableprint = matrix(NA, nrow = 6, ncol = 6)
colnames(tableprint) = c("Fit Index", "Model 1", "Model 2", 
                         "Model 3", "Model 4", "Model 5")
##replace the 1:5 with the appropriate numbers
tableprint[1, ] = c("Chi-square", 1:5)
tableprint[2, ] = c("df", 1:5)
tableprint[3, ] = c("RMSEA", 1:5)
tableprint[4, ] = c("SRMR", 1:5)
tableprint[5, ] = c("CFI", 1:5)
tableprint[6, ] = c("Change", "na", 1:4)

kable(tableprint)

```

## Create a table of the loadings and results.
```{r loadings}
library(knitr)
tableprint = matrix(NA, nrow = 6, ncol = 6)
colnames(tableprint) = c("Loading", "Model 1", "Model 2", 
                         "Model 3", "Model 4", "Model 5")
##replace the 1:5 with the appropriate numbers, or the XXs for the residuals
tableprint[1, ] = c("Residuals", 1:4, "1: XX, 2: XX, 3: XX, 4: XX, 5: XX")
tableprint[2, ] = c("Intercept Mean", 1:5)
tableprint[3, ] = c("Intercept Variance", 1:5)
tableprint[4, ] = c("Slope Mean", "na", "na", "na", 1:2)
tableprint[5, ] = c("Slope Variance", "na", "na", 1:3)
tableprint[6, ] = c("Covariance", "na", "na", 1:3)

kable(tableprint)

```

## Interpret your findings:
    Where do people start?
    What is the change over time?
    Which model is the best? 
    What does that imply?