---
title: "9 Full SEM"
author: "erin buchanan"
date: "6/26/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Full SEM Class Assignment

## Create a model of the relationship between the following variables:
    a. University composite (formative): 
        i. Class - perception of the way school work, classes, grades, and other related academic goals are going for a student.
        ii.	Social - perception of social networks, friendships, support systems, and connectedness on campus.
        iii.	Learning - perception of student's happiness with the learning environment on campus (professors, academic support, fit with major, etc.).
    b. 	Psychological factor (reflexive):
        i.	Depression
        ii. Anxiety
        iii.	Stress
    c.	Health factor (reflexive):
        i.	Chronic health issues
        ii. Physical fitness and active health
        iii.	Sexual health
    d.	The university composite should predict both the psychological and health factors. We expect that as university perception changes, changes in mental and physical health symptoms should exist as well. Note: all variables have been scaled so that high scores are bad. 

## Here's the code for the covariance table and names of variables. 

```{r set up code}
library(lavaan)
data.cov = lav_matrix_lower2full(c(169.00, 
                                   73.710,	182.2500,
                                   73.229,	88.4250,	171.6100,
                                   63.375,	72.5625,	127.7250,	156.2500,
                                   42.120,	67.4325,	122.0265,	123.1875,	182.2500,
                                   57.226,	63.2610,	117.1926,	154.4250,	138.0240,	201.6400,
                                   30.875,	32.0625,	60.9805,	62.9375,	76.9500,	79.5910,	90.2500,
                                   36.075,	38.9610,	61.0722,	58.2750,	65.9340,	70.9290,	81.1965,	123.2100,
                                   18.096,	21.1410,	26.2131,	39.1500,	44.6310,	46.9452,	48.7635,	56.0106,	75.6900))
rownames(data.cov) = colnames(data.cov) = c("class", "social", "learn", "chronic", 
                                            "physical", "sex", "dep", "anx", "stress")

```

## Include a picture of your model.
    Interpret the path coefficients. Explain the relationships between the variables. 

## Include the fitMeasures() here. 
    Interpret the fit indices - is the model any good?



