---
title: "10 MGCFA"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MGCFA Class Assignment

Using the same RS14 dataset from class, examine the multigroup analysis using `Ethnicity` as the grouping variable of interest. 

## Data Libraries

Load the included dataset and libraries for this assignment. 

```{r}

```

## Data Cleanup

In this example, code 1 as Black and 2 as White. Be sure to first change the variable to a factor with labels. 

```{r}

```

## Overall CFA

In this section, build the overall one-factor CFA for the RS14. You can use the example we did in class to get started. Include the `cfa()` and `summary()` of your model here. You should call this model `overall.model`.

```{r}

```

## White Overall Summary

Create a `white.fit` of the model for only White participants. Include the `summary()` of this model. 

```{r}

```

## Black Overall Summary

Create a `black.fit` of the model for only Black participants. Include the `summary()` of this model. 

```{r}

```

## Add the fit to table

In the code below, we've started a table for our fit indices. Fill in the section labeled `#update here` with the same `round(fitmeasures(...))` code used in the first row. 

```{r}
library(knitr)
table_fit <- matrix(NA, nrow = 8, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
kable(table_fit)

table_fit[2, ] <- c("White Model", #update here
                    )

table_fit[3, ] <- c("Black Model", #update here
                    )

kable(table_fit)
```

QUESTION: Does your model appear to fit ok overall and within each individual group? 
ANSWER: 

## Configural Invariance

Create a `configural.fit` model using `Ethnicity` as your group variable. Include a `summary()` of this model. Add in the `configural.fit` to your table. 

```{r}


table_fit[4, ] <- c("Configural Model", #update here
                    )

kable(table_fit)
```

## Metric Invariance

In this section, create `metric.fit`, summarize the model, and add the model information to your table. 

```{r}


table_fit[5, ] <- c("Metric Model", #update here
                    )

kable(table_fit)
```

## Scalar Invariance

In this section, create `scalar.fit`, summarize the model, and add the model information to your table.  

```{r}

table_fit[6, ] <- c("Scalar Model", #update here
                    )

kable(table_fit)
```

## Strict (Error) Invariance

Last, add `strict.fit` by including error variances in your multigroup model, summarize that model, and include the fit information in the table. 

```{r}

table_fit[7, ] <- c("Strict Model", #update here
                    )

kable(table_fit)
```

QUESTION: Looking at your results, do you see anywhere that indicates non-invariance (i.e., has a larger change than CFI = .01)? Where did it appear to break down?
ANSWER:

## Partial Invariance

Use the code provided from class to calculate the potential pathway that should be freed to improve our model fit for partial invariance. 

```{r}

```

## Update the Model

Create `partial.fit` by updating your model to allow for the freed parameter. Summarize the model, and add this model's fit information to your table. 

```{r}

table_fit[8, ] <- c("Partial Model", #update here
                    )

kable(table_fit)
```

QUESTION: Does the freeing of this one parameter bring your model up to partial invariance for that step? 
ANSWER:

QUESTION: What does the result of the partial invariance step imply for interpreting this scale? 
ANSWER: