---
title: "Multi-Group Confirmatory Factor Analysis"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
output: 
  slidy_presentation:
    incremental: true 
---

```{r echo = F, message = F, warning = F}
knitr::opts_chunk$set(echo = TRUE)
library(lavaan)
library(semPlot)
```

## Multigroup Models

- Let's start with some terminology specific to multigroup models: invariance = equivalence 
- Under different conditions, do the measurements yield the same measurement of attributes?
- Generally, we've seen that latent variable models are estimating the data based on the covariances. For these models, we will also add the mean structure. 
- While you can test many groups in these models, you will want to generally compare two at a time. 

## Mean Structure

- Mean structure represents the intercept of our manifest variables 
- In regression, remember that the Y-intercept is the mean of Y (given X = 0 or no X variables)
  - That's your best guess for what someone is going to score on that item without any other X information
  - Same idea in a latent variable model - it's the starting value for that manifest variable.

## Latent Means

- Latent means are the estimated score on the latent variable for participants.
- It's a weighted score of each item's original value with their path coefficient, and all items are averaged together. 
- We can use `lavPredict()` to calculate these for us.

## Multigroup Questions

- Do items act the same across groups?
- Is the factor structure the same across groups?
- Are the paths equal across groups?
- Are the latent means equal across groups?

## How to MG

- First, test the model as a regular CFA with everyone in the dataset 
  - This model will tell you if you have problems with your CFA
  - This model is the least restrictive
  - Do not use grouping variables

## How to MG

- Second, test each group separately with the same CFA structure to determine that each individual group fits ok. 
- Fit indices often decrease slightly here, because sample size is smaller (which usually has a bit more error variance).
- Mainly, you are looking for models that completely break down 
  - You could have a poor fitting CFA overall and use this step to see if that's because one group just does not fit. 
  
## How to MG  

- The next steps will be to nest the two models together.
- Nesting is like stacking the models together (like pancakes).
- For the nested model steps, most people use Brown’s terminology and procedure.

## How to MG

- All the possible paths:
  - The whole model (the picture)
  - Loadings (regression weights)
  - Intercepts (y-intercept for each item)
  - Error variances (variance)
  - Factor variances (variances for the latents)
  - Factor covariances (correlation)
  - Factor means (latent means)

## Equal Form / Configural Invariance

- In this model, you put the two groups together into the same model.
- You do not force any of the paths to be the same, but you are forcing the model picture to be the same.
- You are testing if both groups show the same factor structure (configuration).

## Metric Invariance

- In this model, you are forcing all the factor loadings (regression weights) to be exactly the same.
- This step will tell you if the groups have the same weights for each question – or if some questions have different signs or strengths.

## Scalar Invariance

- In this model, you are forcing the intercepts of the items to be the same.
- This step will tell you if items have the same starting point – remember that the y-intercept is the mean of the item.
- If a MG model is going to indicate non-invariance – this step is often the one that breaks.

## Strict Factorial Invariance

- In this model, you are forcing the error variances for each item to be the same. 
- This step will tell you if the variance (the spread) of the item is the same for each group.  
- If you get differences, that indicates one group has a larger range of answers than another, which indicates they are more heterogeneous. 

## Other Steps

- Most of the previous steps are on the manifest/measured variables only.
- Generally, we focus on those because they indicate performance of the scale.
- Population Heterogeneity:
  - Equal factor variances: Testing if latents have the same set of variance – means that the overall score has the same spread
  - Equal factor covariances: Testing if the correlations between factors is the same for each group
  - Equal latent means: Testing if the overall latent means are equal for each group

## How to Judge

- How can I tell if steps are invariant?
- You will expect fit to get worse as you go because you are being more and more restrictive.
- While we can use change in $\chi^2$, most suggest a change in CFI > .01 to be a difference in fit. 

## Model Breakdown

- What do I do if steps are NOT invariant?
- Partial invariance – when strict invariance cannot be met, you can test for partial invariance
- Partial invariance occurs when most of the items are invariant but a couple.
- You have to meet the invariance criteria, so you trying to bring your bad model "up" to the invariant level
- You want to do as few of items as possible

## Partial Invariance

- So, how do I test partial invariance?
- We can use modification indices to see which paths are the most problematic.
- You will change ONE item at a time.
- Slowly add items to bring CFI up to an acceptable change level (i.e. .01 or less change from the previous model). 

## Test Latent Means

- After saying the measured variables are partially to fully invariant, sometimes people also calculate latent means and use *t*-tests to determine if they are different by groups. 
  - Instead of doing all the population heterogeneity steps. 
- At the minimum, it is useful to know how to calculate a weighted score for each participant.
- We normally use EFA/CFA to show that each question has a nice loading and the questions load together
- And then we use subtotals or averages to create an overall score for each latent 
  - This procedure totally ignores the fact that loadings are often different.
  - Why lose that information?
  
## Let's get started!

- Equality constraints
- We've talked before about setting paths equal to each other by calling them the same parameter name
  - `cheese =~ a\*feta + a\*swiss`
  - So feta and swiss will be estimated at the same value. 
- The entire purpose of a multigroup model is to build equality constraints
- A few packages used to do this ... but have become more trouble than they are worth, so let's look at how to do these steps with just `lavaan`. 

## An Example

- Using the RS-14 scale: a one-factor measure of resiliency

```{r}
library(lavaan)
library(rio)
res.data <- import("assignment_mgcfa.csv")

head(res.data)
```

## Clean up the data

- By not including other labels, we are dropping those categories 

```{r}
table(res.data$Sex)
res.data$Sex <- factor(res.data$Sex, 
                       levels = c(1,2),
                       labels = c("Men", "Women"))
res.data <- subset(res.data, !is.na(Sex))
nrow(res.data)
```

## Start with Overall CFA

- NEW: `meanstructure = TRUE`
- Gives you the intercepts and means in the model.
- You want to turn that one at the beginning, and you are first examining models with means, so you can tell if you have bad parameters at the start. 

## Start with Overall CFA

```{r}
overall.model <- '
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
'

overall.fit <- cfa(model = overall.model,
                   data = res.data, 
                   meanstructure = TRUE) ##this is important 
```

## Examine Overall Fit

```{r}
summary(overall.fit, 
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Make a table of fit indices

```{r}
library(knitr)
table_fit <- matrix(NA, nrow = 9, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
kable(table_fit)
```

## Create a Picture

```{r semplot, messages = F}
library(semPlot)

semPaths(overall.fit, 
         whatLabels = "std", 
         edge.label.cex = 1,
         layout = "tree")
```

## Men Overall Summary

```{r}
men.fit <- cfa(model = overall.model,
               data = res.data[res.data$Sex == "Men" , ], 
               meanstructure = TRUE)
summary(men.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Women Overall Summary

```{r}
women.fit <- cfa(model = overall.model,
                 data = res.data[res.data$Sex == "Women" , ], 
                 meanstructure = TRUE)
summary(women.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[2, ] <- c("Men Model", round(fitmeasures(men.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Women Model", round(fitmeasures(women.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Configural Invariance

- Both groups "pancaked" together 

```{r}
configural.fit <- cfa(model = overall.model,
                      data = res.data,
                      meanstructure = TRUE,
                      group = "Sex")
summary(configural.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[4, ] <- c("Configural Model", round(fitmeasures(configural.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Metric Invariance

- Are the factor loadings the same? 

```{r}
metric.fit <- cfa(model = overall.model,
                  data = res.data,
                  meanstructure = TRUE,
                  group = "Sex",
                  group.equal = c("loadings"))
summary(metric.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[5, ] <- c("Metric Model", round(fitmeasures(metric.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Scalar Invariance

- Are the item intercepts the same? 

```{r}
scalar.fit <- cfa(model = overall.model,
                  data = res.data,
                  meanstructure = TRUE,
                  group = "Sex",
                  group.equal = c("loadings", "intercepts"))
summary(scalar.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[6, ] <- c("Scalar Model", round(fitmeasures(scalar.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Strict (Error) Invariance

- Are the item residuals the same? 

```{r}
strict.fit <- cfa(model = overall.model,
                  data = res.data,
                  meanstructure = TRUE,
                  group = "Sex",
                  group.equal = c("loadings", "intercepts", "residuals"))
summary(strict.fit,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[7, ] <- c("Strict Model", round(fitmeasures(strict.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Partial Invariance

- We can see in this last step that we have a difference in models based on change in CFI. 
- Now, we have to figure out where the problem is and update our model to fix that problem.
- You would only look for problems *in the step you are in*.

## Partial Invariance

- Figure out which level you need:
  - metric `=~` for loadings
  - scalar `~1` for intercepts
  - strict `~~` for variances
- Change each item one at a time and note the changes

## Partial Invariance

```{r}
##write out partial codes
partial_syntax <- paste(colnames(res.data)[3:16], #all the columns
                        "~~", #residuals
                        colnames(res.data)[3:16]) #all columns again 
partial_syntax

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = res.data,
              meanstructure = TRUE,
              group = "Sex",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list
which.max(CFI_list)
```

## Free up those paramers!

```{r}
strict.fit2 <- cfa(model = overall.model,
                  data = res.data,
                  meanstructure = TRUE,
                  group = "Sex",
                  group.equal = c("loadings", "intercepts", "residuals"), 
                  group.partial = c("RS9 ~~ RS9"))
summary(strict.fit2,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[8, ] <- c("Strict Model RS9", round(fitmeasures(strict.fit2, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Find one more free parameter

- We want to see if we can get up to .902 - .01 = .892 for our CFI. 

```{r}
for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = res.data,
              meanstructure = TRUE,
              group = "Sex",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = c("RS9 ~~ RS9", partial_syntax[i]))
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list
which.max(CFI_list)
```

## Add one more free parameter

```{r}
strict.fit3 <- cfa(model = overall.model,
                  data = res.data,
                  meanstructure = TRUE,
                  group = "Sex",
                  group.equal = c("loadings", "intercepts", "residuals"), 
                  group.partial = c("RS9 ~~ RS9", "RS13 ~~ RS13"))
summary(strict.fit3,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Partial Invariance Met!

```{r}
table_fit[9, ] <- c("Strict Model RS9 + 13", round(fitmeasures(strict.fit3, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Interpretation

- The RS is mostly invariant – the structure, loadings, intercepts, and most of the error variances are the same across men and women.
- However, two items show larger variances:
    - RS9
    - RS13
    - Where, women show much larger variances on both of those questions. 
        - I keep interested in things.
        - My life has meaning. 

## lavPredict on the items

```{r}
predicted_scores <- lavPredict(strict.fit3, type = "ov")

table(res.data$Sex)

predicted_scores <- as.data.frame(do.call(rbind, predicted_scores))
predicted_scores$Sex <- c(rep("Women", 266), rep("Men", 244))

predicted_scores$sum <- apply(predicted_scores[ , 1:14], 1, sum)
head(predicted_scores)

tapply(predicted_scores$sum, predicted_scores$Sex, mean)
```

## lavPredict on the factor scores

```{r}
res.data$sum <- apply(res.data[ , 3:16], 1, sum)

tapply(res.data$sum, res.data$Sex, mean)

latent_means <- lavPredict(strict.fit3)

latent_means <- as.data.frame(do.call(rbind, latent_means))
latent_means$Sex <- c(rep("Women", 266), rep("Men", 244))

options(scipen = 999)
tapply(latent_means$RS, latent_means$Sex, mean) 

tapply(latent_means$RS, latent_means$Sex, mean) * #latent mean
  tapply(res.data$sum, res.data$Sex, sd, na.rm = T) + #real sum
  tapply(res.data$sum, res.data$Sex, mean, na.rm = T) #real sd
```

## Calculate your favorite stat

```{r effectsize, message = F}
library(MOTE)
M <- tapply(predicted_scores$sum, predicted_scores$Sex, mean)
SD <- tapply(predicted_scores$sum, predicted_scores$Sex, sd)
N <- tapply(predicted_scores$sum, predicted_scores$Sex, length)

effect_size <- d.ind.t(M[1], M[2], SD[1], SD[2], N[1], N[2], a = .05)
effect_size$estimate
effect_size$statistic
```

## Summary

- In this lecture you've learned:
  
  - The concepts and terminology for a multigroup model
  - How to implement a multigroup model
  - How to assess for partial invariance
  - How to assess latent means and their potential differences 