---
title: "MGCFA Example"
author: "Erin M. Buchanan"
date: "9/17/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Overview

- This video covers an example of Multigroup Confirmatory Factor Analysis (MGCFA)
- This video is part of my structural equation modeling series:
  - https://www.youtube.com/watch?v=JEFMdQrXwJc&list=PLw93TUuxrFAZkJVc5dhgTZpOT7qmTjlT7
  - https://www.youtube.com/watch?v=tmpFrygKTUQ&list=PLw93TUuxrFAZV3ZgsNfMFszE8OA744NnQ
- This video is an update because of changes in the *semTools* package, as well new information on equivalence testing

## Assumptions

- You know something about structural equation modeling
- You've got an idea about multigroup models 
  - Lecture: https://youtu.be/W4fkW-tqIUg
- You've learned a bit of *lavaan* syntax 

## Let's get started!

- Equality constraints
- We've talked before about setting paths equal to each other by calling them the same parameter name
  - cheese =~ a\*feta + a\*swiss
  - So feta and swiss will be estimated at the same value. 
- The entire purpose of a multigroup model is to build equality constraints
- We could do this one at a time, ourselves, or use the *semTools* package to build these

## An Example

- Using the RS-14 scale: a one-factor measure of resiliency

```{r}
##libraries
library(lavaan)

##data
master <- read.csv("mgcfa RS.csv")

head(master)
```

## Clean up the data

- By not including other labels, we are dropping those categories 

```{r}
master$Sex <- factor(master$Sex, 
                     levels = c(1,2),
                     labels = c("Men", "Women"))
table(master$Sex)

master <- subset(master, 
                 !is.na(Sex))
```

## Start with Overall CFA

- NEW: `meanstructure = TRUE`
- Gives you the intercepts and means in the model.
- You want to turn that one at the beginning, and you are first examining models with means, so you can tell if you have bad parameters at the start. 

## Start with Overall CFA

```{r}
overall.model <- '
RS =~ RS1 + RS2 + RS3 + RS4 + RS5 + RS6 + RS7 + RS8 + RS9 + RS10 + RS11 + RS12 + RS13 + RS14
'

overall.fit <- cfa(model = overall.model,
                   data = master, 
                   meanstructure = TRUE) ##this is important 
```

## Examine Overall Fit

```{r}
summary(overall.fit, 
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Make a table of fit indices

```{r}
table_fit <- matrix(NA, nrow = 9, ncol = 6)
colnames(table_fit) = c("Model", "X2", "df", "CFI", "RMSEA", "SRMR")
table_fit[1, ] <- c("Overall Model", round(fitmeasures(overall.fit, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))
kable(table_fit)
```

## Create a Picture

```{r semplot, messages = F}
library(semPlot)

semPaths(overall.fit, 
         whatLabels = "std", 
         layout = "tree")
```

## The `equaltestMI` package 

```{r}
library(equaltestMI)

MG.model <- eqMI.main(model = overall.model, 
                      data = master,
                      group = "Sex",
                      meanstructure = TRUE,
                      output = "both", #mean, covariance, both  
                      equivalence.test = FALSE, #change this in a moment
                      adjRMSEA = TRUE, #but see new paper
                      projection = TRUE, #see notes
                      bootstrap = FALSE)
```

## Examine and Update Results

- You would first examine each group separately to see fit
- All the models you could potentially want to run are saved with the `eqMI.main` function
- Let's work through the Brown style steps to see how we can pull all the information we'd want

## Men Overall Summary

```{r}
##Men
summary(MG.model$convention.sem$LavaanOut$fit.configural.g1, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Women Overall Summary

```{r}
##Women
summary(MG.model$convention.sem$LavaanOut$fit.configural.g2, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[2, ] <- c("Men Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.configural.g1, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

table_fit[3, ] <- c("Women Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.configural.g2, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Configural Invariance

- Both groups "pancaked" together 

```{r}
summary(MG.model$convention.sem$LavaanOut$fit.combine.groups, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[4, ] <- c("Configural Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.combine.groups, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## What is this doing?

- Two places to change things: 1) model definition, 2) `cfa()` parameters

```{r}
overall.model

#cfa(model = overall.model, 
#   data = master,
#   meanstructure = TRUE,
#   group = "Sex")

MG.model$convention.sem$LavaanOut$fit.combine.groups@call
```

## Metric Invariance

- Are the factor loadings the same? 

```{r}
summary(MG.model$convention.sem$LavaanOut$fit.metric, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[5, ] <- c("Metric Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.metric, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## What is this doing?

```{r}
overall.model

#cfa(model = overall.model, 
#   data = master,
#   meanstructure = TRUE,
#   group = "Sex",
#   group.equal = c("loadings"))

MG.model$convention.sem$LavaanOut$fit.metric@call
```

## Scalar Invariance

- Are the item intercepts the same? 

```{r}
summary(MG.model$convention.sem$LavaanOut$fit.scalar, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[6, ] <- c("Scalar Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.scalar, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## What is this doing?

```{r}
overall.model

#cfa(model = overall.model, 
#   data = master,
#   meanstructure = TRUE,
#   group = "Sex",
#   group.equal = c("loadings", "intercepts"))

MG.model$convention.sem$LavaanOut$fit.scalar@call
```

## Strict (Error) Invariance

- Are the item residuals the same? 

```{r}
summary(MG.model$convention.sem$LavaanOut$fit.strict.residuals, ##each model saved here
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[7, ] <- c("Strict Model", round(fitmeasures(MG.model$convention.sem$LavaanOut$fit.strict.residuals, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## What is this doing?

```{r}
overall.model

#cfa(model = overall.model, 
#   data = master,
#   meanstructure = TRUE,
#   group = "Sex",
#   group.equal = c("loadings", "intercepts", "residuals"))

MG.model$convention.sem$LavaanOut$fit.strict.residuals@call
```

## Partial Invariance

- We can see in this last step that we have a difference in models based on change in CFI. 
- Now, we have to figure out where the problem is and update our model to fix that problem.
- You would only look for problems *in the step you are in*.

## Partial Invariance

- Figure out which level you need:
  - metric `=~` for loadings
  - scalar `~1` for intercepts
  - strict `~~` for variances
- Change each item one at a time and note the changes

## Partial Invariance

```{r}
##write out partial codes
partial_syntax <- paste(colnames(master)[4:17], #all the columns
                        "~~", #residuals
                        colnames(master)[4:17]) #all columns again 

CFI_list  <- 1:length(partial_syntax)
names(CFI_list) <- partial_syntax

for (i in 1:length(partial_syntax)){
  
  temp <- cfa(model = overall.model, 
              data = master,
              meanstructure = TRUE,
              group = "Sex",
              group.equal = c("loadings", "intercepts", "residuals"),
              group.partial = partial_syntax[i])
  
  CFI_list[i] <- fitmeasures(temp, "cfi")
}

CFI_list
```

## Figure out which parameters to "free"

```{r}
options(scipen = 999)
sort(CFI_list - fitmeasures(MG.model$convention.sem$LavaanOut$fit.strict.residuals, "cfi"), decreasing = T)
```

## Free up those paramers!

```{r}
MG.model_2 <- eqMI.main(model = overall.model, 
                      data = master,
                      group = "Sex",
                      meanstructure = TRUE,
                      group.partial = c("RS9~~RS9"),
                      output = "both", #mean, covariance, both  
                      equivalence.test = FALSE, #change this in a moment
                      adjRMSEA = TRUE, #but see new paper
                      projection = TRUE, #see notes
                      bootstrap = FALSE,
                      quiet = T)

MG.model_2$convention.sem$LavaanOut$fit.strict.residuals@call
```

## Check out the fit

```{r}
summary(MG.model_2$convention.sem$LavaanOut$fit.strict.residuals,
        standardized = TRUE, 
        rsquare = TRUE, 
        fit.measure = TRUE)
```

## Add the fit to table

```{r}
table_fit[8, ] <- c("Strict Model RS9", round(fitmeasures(MG.model_2$convention.sem$LavaanOut$fit.strict.residuals, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Add one more free parameter

```{r}
MG.model_3 <- eqMI.main(model = overall.model, 
                      data = master,
                      group = "Sex",
                      meanstructure = TRUE,
                      group.partial = c("RS9~~RS9", "RS13~~RS13"),
                      output = "both", #mean, covariance, both  
                      equivalence.test = FALSE, #change this in a moment
                      adjRMSEA = TRUE, #but see new paper
                      projection = TRUE, #see notes
                      bootstrap = FALSE,
                      quiet = T)

table_fit[9, ] <- c("Strict Model RS9 + 13", round(fitmeasures(MG.model_3$convention.sem$LavaanOut$fit.strict.residuals, 
                                                 c("chisq", "df", "cfi",
                                                   "rmsea", "srmr")),3))

kable(table_fit)
```

## Interpretation

- The RS is mostly invariant – the structure, loadings, intercepts, and most of the error variances are the same across men and women.
- However, two items show larger variances:
    - RS9
    - RS13
    - Where, women show much larger variances on both of those questions. 
        - I keep interested in things.
        - My life has meaning. 

## lavPredict on the items

```{r}
predicted_scores <- lavPredict(MG.model_3$convention.sem$LavaanOut$fit.strict.residuals,
                               type = "ov")

table(master$Sex)

predicted_scores <- as.data.frame(do.call(rbind, predicted_scores))
predicted_scores$Sex <- c(rep("Women", 266), rep("Men", 244))

predicted_scores$sum <- apply(predicted_scores[ , 1:14], 1, sum)

tapply(predicted_scores$sum, predicted_scores$Sex, mean)
```

## lavPredict on the factor scores

```{r}
master$sum <- apply(master[ , 4:17], 1, sum)

tapply(master$sum, master$Sex, mean)

latent_means <- lavPredict(MG.model_3$convention.sem$LavaanOut$fit.strict.residuals)

latent_means <- as.data.frame(do.call(rbind, latent_means))
latent_means$Sex <- c(rep("Women", 266), rep("Men", 244))

tapply(latent_means$RS, latent_means$Sex, mean) 

tapply(latent_means$RS, latent_means$Sex, mean) * tapply(master$sum, master$Sex, sd, na.rm = T) + tapply(master$sum, master$Sex, mean, na.rm = T)
```

## Calculate your favorite stat

```{r effectsize, message = F}
library(MOTE)
M = tapply(predicted_scores$sum, predicted_scores$Sex, mean)
SD = tapply(predicted_scores$sum, predicted_scores$Sex, sd)
N = tapply(predicted_scores$sum, predicted_scores$Sex, length)

d.ind.t(M[1], M[2], SD[1], SD[2], N[1], N[2], a = .05)
```

## Compare that to your latent means output

```{r}
MG.model_3$projection.res$projection$latent.test
```

## EQ Testing?

```{r}
EQ.model <- eqMI.main(model = overall.model, 
                      data = master,
                      group = "Sex",
                      meanstructure = TRUE,
                      output = "both", #mean, covariance, both  
                      equivalence.test = TRUE, #change this in a moment
                      adjRMSEA = TRUE, #but see new paper
                      projection = TRUE, #see notes
                      bootstrap = FALSE,
                      quiet = T)

EQ.model$eqMI.stat
```

## Thanks!



