---
title: "12 IRT"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dichotomous IRT Class Assignment

The included dataset includes data from an Educational Psychology Test scored as 0 (answered incorrectly) and 1 (answered correctly). Import the data (assignment_dirt.csv) and libraries below. 

```{r}

```

## Two Parameter Logistic

Include a 2PL calculated on just columns V2 through V5. Save the model as `edu.model`. Use the `coef()` function to examine the difficulty and discrimination parameters. 

```{r}

```

## 2PL Plots

Include the ICC and TIF plots to view all the items and overall test information at once. 

```{r}

```

## Three Parameter Logistic

Include the 3PL model as `edu2.model`. Use the `coef()` function to examine the difficulty, discrimination, and guessing parameters. 

```{r}

```

## 3PL Plots

Include the ICC and TIF plots to view all the items and overall test information at once. 

```{r}

```

## Compare Models

Use the `anova()` function to compare the two models. 

```{r}

```

QUESTION: Which model was better? Does it appear that the guessing parameter adds something useful to the model? 
ANSWER:

QUESTION: Which items would be considered good items based on discrimination?
ANSWER:

## Polytomous IRT 

Load the assignment_mirt data below. You should reverse code items 5, 8, and 13 using `8 - columns` to ensure all items are in the same direction. The scale included examines evaluations of job candidates rated on 15 different qualities. 

```{r}

```

## Graded Partial Credit Model

Create a graded partial credit model to analyze the scale, and save this model as `gpcm.model`. Include the `coef()` for the model to help you answer the questions below. 

```{r}

```

## GPCM Plots

Include the ICC and TIF plots to view all the items and overall test information at once. 

```{r}

```

QUESTION: Examine the items. Do they appear ordered where each answer function is ordered correctly from 1 to 7?
ANSWER:

QUESTION: Examine the items. Do we need all 7 items on this scale? (i.e., do they all have the probability of being the most likely answer choice?)
ANSWER:

QUESTION: Which items indicate good discrimination? 
ANSWER:
        


