---
title: 'Set Up Virtual Machine'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

## Install Software

- Most recent version of R: https://cloud.r-project.org/
- Most recent version of RStudio: https://rstudio.com/products/rstudio/download/#download

```{r}
##r chunk - do not change these
R.version
#RStudio.Version() run this line but it won't knit with it "on"
```

What version of Rstudio are you using?

## Set up your python

- Install the `reticulate` package (do not include this code).
- Load the `reticulate` library.

```{r python_setup}
##r chunk

```

## Install Miniconda

Try typing `py_config()` below. You should get a prompt to install Miniconda. If not, use `install_miniconda()`.

```{r}
##r chunk

```

## Show you've installed Python

Run `py_config()` in the *R* chunk below. 

```{r}
##r chunk

```

## Let's do some R

- In this chunk, we will load a dataset - use `data(rock)` to load it. 
- Use the `head()` function to print out the first six rows of the dataset. 

```{r an_r_section}
##r chunk

```

## Let's do some Python

- First, let's install some packages. 
- You will need `numpy`, `nltk`, `spacy`, `scikit-learn` and `pandas` for starters. 
- You can check if you have them first by using `py_module_available("PACKAGE")`.
- Note: `scikit-learn` is a special package, you can check if it's avaliable by using `sklearn` but you install it with `scikit-learn`. 

```{r check_install}
##r chunk

```

- If any of these return `FALSE`, then install them using `py_install("PACKAGE")`. If you receive an error saying it cannot be found on Minicode, use `py_install("PACKAGE", pip = T)`.

```{r install_packages}
#if they are all TRUE, leave this blank
##r chunk

```

## Call a dataset in Python

- First, load the `sklearn` library, it has several sample datasets. You load python packages by using `import PACKAGE`. Note that you install and call this package different names (scikit-learn = sklearn).
- Next, import the datasets part of sklearn by doing `from PACKAGE import FUNCTION`. Therefore, you should use `from sklearn import datasets`. 
- Then call the `boston` dataset by doing: `dataset_boston = datasets.load_boston()`.
- To print out the first six rows, use the `.head()` function: `df_boston.head()`, after converting the file with `pandas` (code included below).

```{python}
##python chunk
##TYPE HERE##

##convert to pandas
import pandas as pd
df_boston = pd.DataFrame(data=dataset_boston.data, columns=dataset_boston.feature_names)
```

QUESTION: Look in your environment window. What do you see?

## Print out Python information in R

- You can have the two environments interact. To print out information from Python in R: `py$VARNAME`.
- Normally, to print out R dataset columns, you do `DATAFRAME$COLUMN`. Try to print out the `CRIM` column from your `df_boston` variable. 

```{r}
##r chunk

```

## Print our R in Python

- When using R in Python, instead of `$`, we use `.` like this: `r.VARNAME`. 
- To print out a single column, you use `DATAFRAME["COLUMNNAME"]`. Try printing out the `shape` column in the `rock` dataset. 

```{python}
##python chunk

```

## Get started with PyCharm!

- Great job! Here's what you learned:
  - Installed Python!
  - You know how to install and load the libraries in both languages.
  - You know how to load built in datasets in both languages.
  - You know how to print out data from one language to another. 
- Turn this document in for credit --> hit KNIT --> turn in the HTML file.
- Be sure to fill in your name at the top!
- Be sure to answer the embedded questions!

  

