---
title: "MLM Logistic Regression"
author: "Erin M. Buchanan"
date: "9/3/2019"
output: slidy_presentation
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(RCurl)
library(lme4)

##graph clean up code
cleanup = theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"), 
              legend.key = element_rect(fill = "white"),
              text = element_text(size = 15))
```

## About the Video

- This video covers multilevel logistic regression, assuming you understand a few things:
  - You know a little bit about logistic regression.
  - You know a little bit about multilevel models.
  - You know a good bit about R. 
  
## About the Video

- If those aren't true, try checking out:
  - MLM Videos: I have a few lectures, workshop, and examples: https://www.youtube.com/channel/UCMdihazndR0f9XBoSXWqnYg/search?view_as=subscriber&query=multilevel
  - Logistic Videos: Lectures and examples: https://www.youtube.com/channel/UCMdihazndR0f9XBoSXWqnYg/search?view_as=subscriber&query=logistic
  - Learn R: See week 1 software overview: http://statstools.com/learn/advanced-statistics/

## About the Data

- We are going to use data from a project that's currently under review about reporting rates of outliers.
- You can find it and the preprint linked to our Open Science page: https://osf.io/52mqw/.

## Load the Data

```{r}
data_url <- getURL("https://raw.githubusercontent.com/doomlab/Outliers/master/paper/outliers%20complete.csv")
master <- read.csv(text = data_url)
names(master)
```

## General Steps

- Data screening
  - Accuracy
  - Missing
  - Outliers*
  - Assumptions:
    - Independence 
    - Multicollinearity
    - DV Ratios

## Data Screening

- Accuracy + missing data 
- Outliers?

```{r}
##clean up the mention column 
master$mention.outliers = factor(master$mention.outliers,
                      levels = c("no", "yes"),
                      labels = c("No", "Yes"))

summary(master$mention.outliers)
```

## Assumptions

- Multicollinearity
- DV Ratios

```{r}
summary(master$mention.outliers)

table(master$Type, master$mention.outliers)

table(master$time.pulled, master$mention.outliers)
```

## Assumptions

- Independence: in this dataset we have both `Journal` and `Article` as structured variables. 
- We can control for the non-independence by using a multilevel model. 

## Visualize the Data

```{r}
##create a data frame of the percentages by time and type
outsummary = table(master$mention.outliers, master$time.pulled, master$Type)
outsummary = as.data.frame(outsummary)
colnames(outsummary) = c("mention.outliers", "time.pulled", "Type", "Freq")

outpercent = as.data.frame(group_by(outsummary, time.pulled, Type) %>%
  mutate(percent = Freq/sum(Freq)*100))

outpercent
```

## Visualize the Data

```{r}
#look at just outliers
graphdata = subset(outpercent, mention.outliers == "Yes")

#calculate CIs to add to graph
graphdata$sample = as.data.frame(table(master$time.pulled, master$Type))$Freq
graphdata$SE = sqrt(graphdata$percent*(100-graphdata$percent)/graphdata$sample)

#make the ggplot
dotplot = ggplot(graphdata, aes(Type, percent, color = time.pulled))
dotplot = dotplot +
  geom_pointrange(aes(ymin=percent-1.96*SE, ymax=percent+1.96*SE)) + 
  xlab("Field of Journal") +
  ylab("Percent of Outlier Mentions") + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  scale_color_manual(name = "Year", 
                     values = c("black", "gray")) + 
  coord_cartesian(ylim = c(0,75)) + 
  cleanup

dotplot
```

## MLM Step 1 

- A completely null model, no effects or random effects 

```{r}
m1 <- glm(mention.outliers ~ 1,
          family = binomial(link="logit"),
          data = master)

summary(m1)
```

## MLM Step 2

- Switch to `glmer`, add random intercept(s) 

```{r}
m2 <- glmer(mention.outliers ~ 1 + (1 | Journal), 
            data = master, 
            family = binomial(link="logit"),
            control = glmerControl(optimizer = "bobyqa"),
            nAGQ = 0)

summary(m2)
```

## MLM Step 2.1

- Add a second random intercept

```{r}
m2.1 <- glmer(mention.outliers ~ 1 + (1 | Journal) + (1 | article), 
            data = master, 
            family = binomial(link="logit"),
            control = glmerControl(optimizer = "bobyqa"),
            nAGQ = 0)

summary(m2.1)
```

## MLM Comparison

```{r}
m1$aic
AIC(logLik(m2))
AIC(logLik(m2.1))
```

## MLM Step 3 

- Add fixed effects

```{r}
m3 <- glmer(mention.outliers ~ year + (1 | Journal) + (1 | article),
            data = master, 
            family = binomial(link="logit"),
            control = glmerControl(optimizer = "bobyqa"),
            nAGQ = 0)

summary(m3)

AIC(logLik(m2.1))
AIC(logLik(m3))
```

## MLM Step 4

- Add random slopes (if you want!)

```{r}
m4 <- glmer(mention.outliers ~ year + (year | Journal) + (1 | article),
            data = master, 
            family = binomial(link="logit"),
            control = glmerControl(optimizer = "bobyqa"),
            nAGQ = 0)

summary(m4)

AIC(logLik(m3))
AIC(logLik(m4))
```

## Why not?

```{r}
dotplot
```

## Thanks for watching!

- Check out these materials: https://osf.io/afqp9/ -> Advanced Stats -> R -> Other Files 
