---
title: "Chapter 14 Homework"
author: "Enter Yo' Name"
date: "10/29/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

The present preliminary trials tested whether undergraduate peer leaders can effectively deliver a dissonance-based eating disorder prevention program, which could facilitate broad dissemination of this efficacious intervention. In Study 1, female undergraduates were randomized to peer-led groups, clinician-led groups, or an educational brochure control condition. Participants in peer- and clinician-led groups showed significantly greater pre–post reductions in eating disorder symptoms than controls, though clinician- versus peer-led groups produced stronger effects at posttest and at 1-year follow-up. Results provide novel evidence that dissonance-based eating disorder prevention groups led by undergraduate peers are feasible and produce greater reductions in eating disorder risk factors and symptoms than minimal-intervention control conditions, but indicate that effects are smaller for peer- versus clinician-led groups.

*Citation:* Stice, E., Rohde, P., Durant, S., Shaw, H., & Wade, E. (2013). Effectiveness of peer-led dissonance-based eating disorder prevention groups: Results from two randomized pilot trials. Behaviour research and therapy, 51(4), 197-206.

# Dataset:

    - Type of prevention program: peer-led, clinician-led, educational brochure
    - Testing time: eating disorder symptoms average, 1-10 scale where low scores indicate fewer symptoms 
        - Pre-test
        - Post-test
        - 1 year follow up

```{r starting}

```

# Questions:
Label the following:

    a.	The between subjects factor:
    b.	The repeated measures factor:
    
What is the dependent variable?

How would you describe this ANOVA?

    a.	#x# = 
    b.	Type of research design = 

# Data Screening:

Assume the data are accurate and there are no missing data points. 

## Outliers:

    a.	Include a summary of your mahal < cutoff scores.
    b.	What are the df for your Mahalanobis cutoff?
    c.	What is the cut off score for your Mahalanobis measure?
    d.	How many outliers did you have?
    e.	Delete all outliers.  

```{r datascreening}

```

# Assumptions:

## Additivity: 

    a.	Include the symnum bivariate correlation table of your continuous measures.
    b.	Do you think you've met the assumption for additivity?
    
```{r additivity}

```

## Linearity: 
    
    a.	Include a picture that shows how you might assess multivariate linearity.
    b.	Do you think you've met the assumption for linearity? 

```{r linearity}

```

## Normality: 
    
    a.	Include a picture that shows how you might assess multivariate normality.
    b.	Do you think you've met the assumption for normality? 

```{r normality}

```

## Homogeneity and Homoscedasticity: 
    
    a.	Include a picture that shows how you might assess multivariate homogeneity and homoscedasticity.
    b.  Include Levene's and Mauchly's Test.
    c.	Do you think you've met the assumption for homogeneity?
    d.  Do you meet the assumption for sphericity?
    e.  If you do not meet the assumption, which correction should you use?
    f.  Do you think you've met the assumption for homoscedasticity?

```{r homogs}

```

# Hypothesis Testing:

## ANOVA

Run a two-way analysis.

    a.	Which effects are significant?
    b.	Calculate the marginal means, and include your output.
    c.	Calculate the conditional means, and include your output.

```{r anova-descriptives}

```

## Graph 

Include a figure of the interaction, and be sure to check the following:
    
    a.	X-Axis Label/Group Labels
    b.	Legend and Labels
    c.	Y-Axis Label
    d.	Error Bars

```{r graph}

```

## Simple effects analysis:
    
    a.	What type of test statistic would you use?
    b.	What post hoc correction would you use?

```{r posthoc}

```

## Effect size:

Calculate a measure of effect size for three of the pairwise comparisons. 

```{r effectsize}

```

## Write Up 

Include a write up of the results of your study.  Things to include:
    
    a.	Brief description of the variables.
    b.	Type of analysis used (i.e. ANOVA).
    c.	Test statistics for both main effects and interaction.
    d.	Test statistics for three of your post hoc tests.
    e.	List which type of error correction you used.
    f.	A reference to your figure.
    g.	Effect sizes for all statistics.
    h.	Two decimal places for statistics.