---
title: "Lesson 13 - Motion Charts"
author: "Erin M. Buchanan"
date: "04/11/2019"
output:
  ioslides_presentation:
    increment: yes
  beamer_presentation:
    incremental: no
---

```{r echo = F}
options(scipen = 999)
```

## Language Topics Discussed

- Language change over time!

## Future Markers

- Future markers are words like *will* and *going to*, which we can examine their change over time
- *Shall* was used for a long time, but it changed over to *will*
- Farming n-grams for trends in the data, like the culturomics lecture
- https://books.google.com/ngrams/graph?content=will%2C+shall%2C+going+to&year_start=1800&year_end=2000&corpus=15&smoothing=3&share=

## Motion Charts

- Allow you to see change over time
- Visualize the relative frequency of different lexemes in constructional slots
- So you could do something like we did in previous lectures over time 

## Motion Charts

- Specifically, we can examine the "territory" of words - when a dominant word in the lexicon is slowly taken over by a synonym
- Using data from Corpus of Historical American English
- Usually these charts are two different collexemes paired with a bunch of words like distinctive collexeme analysis over time

## Motion Charts 

- For this example, we will look at *will* versus *going to* paired with other verbs 
- This analysis will tell us if there is semantic change over time 
- You will use the `googleVis` package, with an internet connection and Flash

## Look at the data

```{r}
library(Rling)
library(googleVis)
data(fut)
head(fut)
```

## Charts

- Words are plotted against each other
- Bubbles show the relative frequencies (like ratios of one to the other) so check out the x and y axis strengths
- You can click the button to watch it over time - slow motion indicates a slow take over versus fast motion meaning a quick change 

## Let's look at a chart!

```{r}
motionchart = gvisMotionChart(fut, idvar = "Verb", timevar = "Period")
plot(motionchart)
```

## Results

- Will is still popular, but slowly changing to going to
- If you pick a specific word, you can view it's trail over time
- Use this to help determine what other analyses you might want to run with logistic regression, etc.

## One more version

```{r}
data(should_ought)
head(should_ought)
```

## Motion chart

```{r}
motionchart2 = gvisMotionChart(should_ought, idvar = "Verb", timevar = "Year")
plot(motionchart2)
```

## Summary

- Learned how to view change in terms over time
- Paired with geographic change charts, we could examine trends in time and space 