---
title: "1 Intro R"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Answer the following questions in provided *R* chunks. 

#	Make a vector of numbers. 

    -	Use the rep or seq function.
    -	Include a concatenate c().

```{r}

```

#	Length
  
     - Use the length() function to figure out how long your vector is.

```{r}

```

#	Matrices
  
     - Make a matrix at least 5 by 5. 
     - Pull out the value for row 2 column 3.
    
```{r}

```

#	Embedded Data
    
    - Use the head() function to look at the dataset USArrests. 
    - Calculate a summary of USArrests.

```{r}

```

#	Data Wrangling

    - Import a data set (attached). 
    - Recode all the values to LEFT and RIGHT in the whichhand column.
    - Create a summary of the dataset.
    - Exclude all NA values in the dataset.
    - Create a dataset with only LEFT handed participants.
    - Calculate the correlation table of just the following variables: LR_switch, finger_switch, rha, word_length, letter_freq

```{r}

```

#	Regression Wrangling:

    - Run a regression using the following: lm(rating~finger_switch, data=data) or whatever you called the data
    - Save the output of the regression.
    - Pull out only the slope from the coefficients.

```{r}

```

