---
title: "Introduction to R"
author: "Erin M. Buchanan"
date: "`r Sys.Date()`"
output: 
  slidy_presentation:
    incremental: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overall Note

- You can learn R.
- You will get frustrated.
- You will get errors that don't help or make sense.
  - Google is your friend.
  - Try Googling the specific error message first.
  - Then try googling your specific function and the error.
  - Try a bunch of different search terms.
    
## Helpful Websites

- Quick-R: www.statmethods.net
- R documentation: www.rdocumentation.org
- Swirl: www.swirlstats.com 
- Stack Overflow: www.stackoverflow.com 
- Learn Statistics with R: https://learningstatisticswithr.com/

## Download Requirements

- Get R: http://cran.r-project.org/ 
- Mac: XQuartz https://www.xquartz.org/ (if you find you do not have it)
- RStudio: http://www.rstudio.org/ 

## Outline

- Commands
- Object Types 
- Subsetting 
- Missing Data
- Working Directories
- Packages 
- Functions

## Commands

- Commands are the code that you tell R to do for you.
- They can be very simple or complex.
- Computers do what *you* tell them to do. Mistakes happen! 
  - Maybe it's a typo, maybe it's a misunderstanding of what the code does 

## Commands

- You can type a command directly into the *console*
- You can type in a document (*Script* or *Markdown*) and tell it to then run in the *console*

```{r}
X <- 4
```

## Commands

- `>` indicates the console is ready for more code
- `+` indicates that you haven't finished a code block
- Capitalization and symbols matter 
- `=` and `<-` are equivalent
- Hit the up arrow – you can scroll through the last commands that were run
- Hit the tab key – you'll get a list of variable names and options to select from
- Use the `?` followed by a command to learn more about it 

## Commands

- Let's take a look and run some simple commands
  - Where is the console
  - How do I move them around?
  - How do I run code?
  - What is a Script?
  - What is Markdown? 
  - How do I run code in those? 

## RStudio

- What are all the windows in RStudio? 
- Working Area:
  - Current files that are open like scripts, markdown, etc. 
- Console, Terminal, Jobs
    - Where the magic happens 
    - Where everything runs
- Environment, History, ...others
  - Tells you what is saved in your *working* environment
  - What variables and types of variables you have made
  - Allows you to click to view them 
- Files, Plots, Packages, Help, Viewer 
  - Shows you a file viewer, pictures/plots, packages, and help!

## Object Types
  
- Here are some of the basics:
  - Vectors
  - Lists
  - Matrices
  - Data Frames
- Within those objects, values can be:
  - Character 
  - Factor (a special type of character)
  - Numeric/Integer/Complex
  - Logical (True, False)
  - NaN (versus NA)
- Last, objects can have attributes (names)

## Objects Example

```{r}
library(palmerpenguins)
data(penguins)
attributes(penguins)
```

## Objects Example

```{r}
str(penguins)

names(penguins) #ls(penguins) provides this as well 
```

## Vectors

- You can think about a vector as one row or column of data
- All the objects must be the same class
- If you try to mix and match, it will coerce them into the same type or make them `NA` if not.

```{r}
X
```

- `[1]` indicates the number of the first item for each printed row 

```{r}
penguins$species
```

## Vector Examples

```{r}
A <- 1:20
A

B <- seq(from = 1, to = 20, by = 1)
B

C <- c("cheese", "is", "great")
C

D <- rep(1, times = 30)
D
```

## Value Types

```{r}
class(A)
class(C)
class(penguins)
class(penguins$species)
```

## Functions Vary 

- Functions are the commands we are running --> things like `class()`, `rep()`
- The code typed into the `()` is called the *arguments*
- Their output varies based on the type of variable you put in the *arguments*

```{r}
dim(penguins) #rows, columns
length(penguins)
length(penguins$species)
```

## Lists

- While vectors are one row of data, we might want to have multiple rows or types
- With a vector, it is *key* to understand they have to be all the same type
- Lists are a grouping of variables that can be multiple types (between list items) and *can be different lengths*
- Often function output is saved as a list for this reason 
- They usually have names to help you print out just a small part of the list

```{r}
output <- lm(flipper_length_mm ~ bill_length_mm, data = penguins)
str(output)
output$coefficients
```

## Dimensional Data

- Matrices
  - Matrices are vectors with dimensions (like a 2X3)
  - All the data *must be the same type*
- Data Frames / Tibbles 
  - Like a matrix, but the columns can be different types of classes

## Matrix

- Let's talk about the `[ , ]` 
- `[row, column]` to *subset* or grab specific values

```{r}
myMatrix <- matrix(data = 1:10,
                   nrow = 5,
                   ncol = 2)
myMatrix
```

## Data Frames

- With data frames, we can use `[ , ]`
- However, they also have attributes that allow us to use the `$` (lists have this too!)

```{r}
penguins[1, 2:3]
penguins$sex[4:25] #why no comma?
```

## Dimensional Data

- What if you want to combine data? We've already talked about `c()`.
- `rbind()` allows you to put together rows
- `cbind()` allows you to put together columns 

```{r}
X <- 1:5
Y <- 6:10
# I can use either because they are the same size 
cbind(X,Y)
rbind(X,Y)
```

## Remind R Where Things Are

- Just because you know we have `penguins` open and there's a variable in in called `species` ... you cannot just use `species`

```{r}
ls()
ls(penguins)
```

## Converting Object Types

- You can use `as.` functions to convert between types
- Show as.<tab> to see what is available 
- Be careful though!

```{r}
newDF <- as.data.frame(cbind(X,Y))
str(newDF)
as.numeric(c("one", "two", "3"))
```

## Subsetting

- Subsetting is parceling out the rows/columns that you need given some criteria.
- We already talked about how to select one row/column with `[1,]` or `[,1]` and the `$` operator.
- What about cases you want to select based on scores, missing data, etc.?

## Subsetting Examples

- How does the logical operator work?
  - It analyzes each row/column for the appropriate logical question 
  - We are asking when bill length is greater than 54 
  - We only got back the rows that the length was greater than 54
  - Careful where you put it (before the `,`)

```{r}
penguins[1:2,] #just the first two rows 
penguins[penguins$bill_length_mm > 54 , ] #how does this work?
penguins$bill_length_mm > 54
```

## Subsetting Examples

```{r}
#you can create complex rules
penguins[penguins$bill_length_mm > 54 & penguins$bill_depth_mm > 17, ]
#you can do all BUT
penguins[ , -1]
#grab a few columns by name
vars <- c("bill_length_mm", "sex")
penguins[ , vars]
```

## Subsetting

```{r}
#another function
#notice any differences? 
subset(penguins, bill_length_mm > 54)
#other functions include filter() in tidyverse
```

## Missing Values

- Missing values are marked with `NA`
- `NaN` stands for not a number, which doesn't automatically convert to missing
- Most functions have an option for excluding the `NA` values *but* they can be slightly different 

```{r}
head(complete.cases(penguins)) #creates logical
head(na.omit(penguins)) #creates actual rows
head(is.na(penguins$body_mass_g)) #for individual vectors
```

## Working Directories

- Your computer has files and folders, and you have to tell *R* where to look
- The working directory is where you are currently telling it to look 

```{r}
getwd()
```

## Working Directory 

- You can set the working directory by doing something like this
- I would suggest this is pretty error prone and breaks when you move files!

```{r}
setwd("/Users/buchanan/OneDrive - Harrisburg University/Teaching/ANLY 580/updated/1 Introduction R")
```
 
## Working Directory

- Working directories are critical because they allow you to automate
- Instead of using the point and click options, you can just run code to open your specific files
- Markdown files are the best!
- Projects are the best! 

## Importing Files

- There are many ways to import files
  - You can use base R functions (`readLines`, `read.csv`)
  - You can use tidyverse (`read_csv`) 
  - You can use Import Dataset clickable option
  - Why not use one package that does most of it like magic?

```{r}
library(rio)
myDF <- import("assignment_introR.csv")
head(myDF)
```

## Packages

- You can install extra functions by installing *packages* or *libraries*
- These can be downloaded from CRAN using `install.packages()`
  - You can also install these by using the Packages tab
- Additional packages can be installed from GitHub and other places

```{r eval = F}
install.packages("car")
```

## Packages 

- View what is installed with the Packages window
- Every time you get a major *R* update, you will likely have to reinstall packages
- Every time you restart *R*, you will need to reload each package
  - Helpful to put the library code right at the top of your scripts 

```{r}
library(car)
```

## Functions

- Functions are pre-written code to help you run analyses
- Get help with function, learn what the arguments should be:
  - Let's flip back to RStudio to see what this did

```{r eval = F}
?lm
help(lm)
```

## Functions

```{r}
args(lm)
example(lm)
```

## Define Your Own Function

- Name the function before `<-`
- Define the arguments inside `()`
- Define what the function does inside `{}`

```{r}
pizza <- function(x){ x^2 }
pizza(3)
```

## Example Functions

```{r}
table(penguins$species)
summary(penguins$bill_length_mm)
```

## Examples Functions with Missing Data

```{r}
mean(penguins$bill_length_mm) #returns NA
mean(penguins$bill_length_mm, na.rm = TRUE)

cor(penguins[ , c("bill_length_mm", "bill_depth_mm", "flipper_length_mm")])
cor(penguins[ , c("bill_length_mm", "bill_depth_mm", "flipper_length_mm")],
    use = "pairwise.complete.obs")
```

## Other Descriptive Functions

- `cov()`
- `var()`
- `sd()`
- `scale()`

## Wrapping Up

- In this demo, you've learned:
  - Some basic programming terminology 
  - Specific *R* defaults and issues
  - Example functions and use cases
- How do I get started? 
  - Practice! 


