---
title: "9 MTMM"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MTMM Practice Assignment

In this example, we will expand our previous example to include one more measurement method of meaning and purpose. The data includes three scales that measure meaning and purpose: The Meaning in Life Questionnaire, the Purpose in Life Questionnaire, and the Seeking of Noetic Goals test. The mapping of traits and methods are:

- Traits:
    - Meaning: 
        - MLQ 1, 2, 5, 10
        - SONG 1, 9
        - PIL 4, 17
    - Purpose:
        - MLQ 3, 4, 6, 8, 9
        - SONG 2, 8
        - PIL 3, 20
- Methods
    - MLQ (m questions)
    - SONG (s questions)
    - PIL (p questions)

## Data and Libraries

Import the data and libraries you need below.

```{r}

```

## Model 1

In this section, build, analyze, and summarize model 1. You can include a diagram if you like, but we will mainly focus on the model building, `cfa()`, and `summary()` in this assignment. 

```{r}

```

## Model 2

In this section, build, analyze, and summarize model 2 for the methods only model. 

```{r}

```

## Model 3

In this section, build, analyze, and summarize model 3 for the perfectly correlated traits model. 

```{r}

```

## Model 4

In this section, build, analyze, and summarize model 4 for the uncorrelated methods model. 

```{r}

```

## Comparisons

We can use `kable()` from the `knitr` library to help us build a table to compare models. You will want to change the `1:5` to the appropriate model step using `fitmeasures` to grab the fit statistics mentioned. An example is provided below. There are lots of ways to make these types of tables, including `broom`. Additionally, `flextable` is a great table package as well. Here's just an example of how one might summarize their models. 

```{r model_table, results = 'asis'}
library(knitr)
tableprint <- matrix(NA, nrow = 4, ncol = 6)
colnames(tableprint) <- c("Model", "Chi-Square", "df", 
                         "RMSEA", "SRMR", "CFI")
##replace the 1:5 with the appropriate code
##the code should be fitmeasures(step1.fit, c("chisq", "df", "rmsea", "srmr", "cfi"))
##add that code for each section
tableprint[1, ] = c("Model 1 - Correlated traits and methods", 1:5)
tableprint[2, ] = c("Model 2 - No traits, correlated methods", 1:5)
tableprint[3, ] = c("Model 3 - Perfectly correlated traits, correlated methods", 1:5)
tableprint[4, ] = c("Model 4 - Correlated traits, uncorrelated methods", 1:5)

kable(tableprint)
```

QUESTION: Using CFI change, what do the model results suggest? For each step note if the models are different, and if that supports/does not support convergent and divergent validity. 
ANSWER MODEL 1 VERSUS MODEL 2:
ANSWER MODEL 1 VERSUS MODEL 3:
ANSWER MODEL 1 VERSUS MODEL 4: 

## Interpreting Parmaters

Print out the `parameterestimates` for Model 1. 

```{r}

```

QUESTION: Are the parameter estimates for the traits higher than the ones for the methods? 
ANSWER:

QUESTION: Examine the correlations between traits. Do the correlations support divergent validity of the traits? 
ANSWER:

QUESTION: Examine the correlation between the methods. Do the correlations support the divergent validity of the methods?
ANSWER: 
