---
title: 'Constituency and Dependency Parsing'
author: "STUDENT NAME"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#do not change this
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries / R Setup

- In this section, include the *R* set up for Python to run. 

```{r}
##r chunk

```

- In this section, include import functions to load the packages you will use for Python.

```{python}
##python chunk

```

## Import the grammar

- Modify `grammar1` from the lecture notes to account for the following sentences:
  - New sentence: "The dog ate the food."
  - New sentence: "The dog walked by the cat in the park." 
  
```{python}
##python chunk

```

## Process the sentences

- Process the sentences with both the `RecursiveDescentParser` and `ShiftReduceParser`.

```{python}
##python chunk

```

## Training Data

- Use *two* of your tweets from the previous assignment and modify the training data for dependency parsing. 

```{python}
##python chunk 

```

## Build the model

- Create a blank spacy pipeline.
- Add the parser to the pipeline.
- Add the labels to the pipeline.

```{python}
##python chunk

```

## Train the model

- Train the model with 10 iterations of the data. 

```{python}
##python chunk

```

## Test the model

- Test your dependency model on a similar tweet.

```{python}
##python chunk

```

## Visualize

- Include a visualization of the tweet you just tested. 
- Remember, you should modify the chunk options to show the picture in the knitted document, since it does not display inline. 

```{python}
##python chunk

```